---
title: "eGRID Production"
author: 
  - "Sean Bock, Abt Global"
  - "Claire Lay, Abt Global"
  - "Justin Stein, Abt Global"
  - "Teagan Goforth, Abt Global"
  - "Emma Russell, Abt Global"
  - "Sara Sokolinski, Abt Global"
  - "Caroline Watson, Abt Global"
  - "Madeline Zhang, Abt Global"
freeze: true
format: 
  html:
    toc: true
    toc-expand: true
    toc-location: left
    html-table-processing: none
    code-fold: true
execute: 
  message: false
  warning: false
params:
  eGRID_year: "2023"
  version: "1.0.1"
  run_demo_file: FALSE # running demographic file takes 4-5 hours
                       # FALSE = default, do not run
                       # TRUE = runs script to collect demographic file
editor: visual
project: 
  execute_dir: project
---

# Overview

This project includes all necessary scripts and documentation to create the Emissions & Generation Resource Integrated Database (eGRID).

# Background

eGRID is a comprehensive source of data from [EPA's Clean Air and Power Division (CAPD)](https://epa.gov/power-sector) on the environmental characteristics of almost all electric power generated in the United States. eGRID is based on available plant-specific data for all U.S. electricity generating plants that provide power to the electric grid and report emissions and electricity data to the U.S. government. Data reported include, but are not limited to, net electric generation; resource mix (the share of generation by resource or fuel type); mass emissions of carbon dioxide (CO<sub>2</sub>), nitrogen oxides (NO<sub>x</sub>), sulfur dioxide (SO<sub>2</sub>), methane (CH<sub>4</sub>), and nitrous oxide (N<sub>2</sub>O); emission rates for CO<sub>2</sub>, NO<sub>x</sub>, SO<sub>2</sub>, CH<sub>4</sub>, and N<sub>2</sub>O; heat input; and nameplate capacity. eGRID reports this information on an annual basis (as well as by ozone season for heat input and NO<sub>x</sub>) at different levels of geographic aggregation.

The final eGRID dataset includes eight levels of data aggregation:

-   **Generator**: A set of equipment that produces electricity and is connected to the U.S. electricity grid.

-   **Unit**: A set of equipment that either produces electricity and is connected to the U.S electricity grid or a set of equipment that is connected to a generator which produces electricity and is connected to the U.S. electricity grid.

-   **Plant**: A facility with one or more units and/or generators that provide power to the electric grid.

-   **State**: U.S. states, Puerto Rico (PR), and the District of Columbia (DC).

-   **Balancing authority**: Regional power system operators that ensure a balance of supply and demand.

-   **eGRID subregion**: EPA defined subregions designed to limit the impacts of the import and export of electricity.

-   **NERC (North American Electric Reliability Corporation) regions**: Each NERC region listed in eGRID represents one of nine regional portions of the North American electricity transmission grid: six in the contiguous United States, plus Alaska, Hawaii, and Puerto Rico (which are not part of the formal NERC regions but are considered so in eGRID).

-   **National U.S.**: Contains all 50 states, Puerto Rico (PR), and the District of Columbia (DC).

Further information on the eGRID methodology can be found in the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

The dataset that this code produces is publicly available [here](https://www.epa.gov/egrid/download-data).

## Using the .qmd file

This is a Quarto (.qmd) file that documents and runs the code necessary to create the eGRID database. Along with sequentially executing the necessary scripts used to create the database, the process is documented throughout, including built-in outputs (e.g., counts of rows, variable names, etc.) and QA steps. This document can be used in two ways: First, when used within an IDE, such as RStudio, it serves as an enhanced master script, allowing users to easily perform each step necessary to create the eGRID database from within a single file. Second, when viewing as a rendered file, it provides thorough documentation of the steps involved in creating eGRID. When rendered, this file provides additional information and tools for navigating the project. The table of contents provides both a convenient look at the project structure and method for navigating the document. There are also hidden code chunks throughout, marked by a button ("Code" with an arrow next to it). Clicking this button reveals the underlying code from the R script that is being sourced in a given section.

# Install Libraries and Set Parameters

Before loading any data or beginning to construct the eGRID database, we install all necessary libraries used in subsequent scripts. Next, the eGRID year is defined, which controls which year of data is loaded from the raw data sources.

## Install required libraries

The script `install_libraries.R` detects all necessary libraries within the project using `renv::dependencies()`, checks for installation, and installs (if needed) and loads into the workspace.

```{r}
#| label: install-libraries.R
#| file: "scripts/install_libraries.R"
#| echo: false
```

```{r}
#| label: load-packages
#| echo: false

library(docstring)
library(dplyr)
library(ggiraph)
library(ggplot2)
library(gt)
library(gtExtras)
library(kableExtra)
library(knitr)
library(patchwork)
library(readxl)
library(stringr)
```

## Define eGRID year

The year of eGRID specified as the parameter "eGRID_year" within the YAML of the Quarto document. When a year value needs to be specified (e.g., when pulling relevant data from the CAMPD API), it is done so by calling `params$eGRID_year`.

**Current year setting: `r params$eGRID_year`**

## Load all helper functions

There are a set of helper functions used throughout the project. These are defined in the folder `scripts/functions`. The `docstring` package is used to provide documentation for functions, similar to typical package documentation. To view the documentation for a given function, run `docstring({function_name})`

```{r}
#| label: load-functions
#| echo: false

# sourcing each file in functions folder
functions <- list.files("scripts/functions")
purrr::walk(paste0("scripts/functions/", functions), ~ source(.x))
```

::: panel-tabset
### Overview

*Click on the tab to view the helper function names.*

### Helper Functions

```{r}
#| label: list-functions
#| echo: false

# listing function names
kable(stringr::str_remove(stringr::str_remove(functions, ".R"), "function_"),
      col.names = c("Helper Functions")) %>%
            kable_styling(full_width = F)
```
:::

# Load Data

## Load data from raw sources

### EPA

The EPA's Clean Air and Power Division (CAPD) contains power plant emissions, compliance, and allowance data. We create and incorporate a composite file from several CAPD sources, containing data about facilities and annual emissions. Specifically, we include data about facility attributes, annual emissions, and annual emissions during ozone months.

These data are available through the [CAPD API](https://www.epa.gov/power-sector/cam-api-portal#/documentation). `data_load_epa.R` downloads the facility attributes and emissions data for a selected year from the CAPD API. These raw files will be combined and cleaned in subsequent steps. For this script to run, an API key is required.

An API key can be requested [here](https://www.epa.gov/power-sector/cam-api-portal#/api-key-signup). Once a key is obtained, paste your key into the file `api_keys/epa_api_key.txt` and save. Once saved, the script `data_load_epa.R` will be able to successfully connect to and load data from the CAPD API.

```{r}
#| label: load-data-epa 
#| file: "scripts/data_load_epa.R" 
#| echo: fenced 
#| error: false 
```

Three data tables are downloaded from the the CAPD and stored into one .RDS file, `epa_raw.RDS`. This file consists of facility attributes, annual emissions data, and containing annual emissions data for the ozone months. See a summary of the raw EPA file below, separated into categories.

#### EPA Raw Tables

```{r}
#| label: create-epa-tables 
#| echo: false  

source("scripts/functions/function_summary_table.R") 

# function to create summary table  
epa_raw <- read_rds(glue::glue("data/raw_data/epa/{params$eGRID_year}/epa_raw.RDS")) 

table_epa_raw <- create_summary_table(epa_raw)  

epa_facilities      <- epa_raw[1:26] 
epa_emissions       <- epa_raw[27:46] 
epa_emissions_ozone <- epa_raw[47:58]  

table_facilities      <- create_summary_table(epa_facilities) 
table_emissions       <- create_summary_table(epa_emissions) 
table_emissions_ozone <- create_summary_table(epa_emissions_ozone)
```

::: panel-tabset
#### Overview

*Click through the tabs above to view files represented from each EPA source.*

**EPA facility attributes**: Columns 1 - 26 of `epa_raw.RDS`.

**EPA annual emissions**: Columns 27 - 47 of `epa_raw.RDS`.

**EPA ozone season emissions**: Columns 47 - 58 of `epa_raw.RDS`. The ozone season is defined as May through September.

#### EPA facility attributes

```{r}
#| label: print-epa-tab-facilities 
#| echo: false  

table_facilities
```

#### EPA annual emissions

```{r}
#| label: print-epa-tab-emissions 
#| echo: false  

table_emissions
```

#### EPA ozone season emissions

```{r}
#| label: print-epa-tab-emissions-ozone 
#| echo: false  

table_emissions_ozone
```
:::

### EIA

The U.S. Energy Information Administration (EIA), a part of the Department of Energy, collects and maintains energy-related data for policy making and for the public. eGRID integrates several EIA data forms into its database for relevant values.

As of 2024, the EIA API does not contain the most detailed data available, which is necessary for the construction of eGRID. More detailed data for the EIA forms [923](https://www.eia.gov/electricity/data/eia923/), [860](https://www.eia.gov/electricity/data/eia860/), and [861](https://www.eia.gov/electricity/data/eia861/) are available as zipped excel file downloads on the EIA website. `data_load_eia.R` creates a new folder in the project folder called "raw_data". The zip files for each of the forms are downloaded and unzipped within this newly created folder. Each excel file contains several sheets that serve as the raw EIA data sources used to create eGRID.

```{r}
#| label: data-load-eia
#| file: "scripts/data_load_eia.R"
#| error: false
#| echo: fenced
```

The tables within EIA Files and Sheets display each of the unzipped raw files across the three EIA forms, including the sheets embedded within.

```{r}
#| label: custom-gt-print
#| echo: false

knit_print.gt <- function(x, ...) {
  stringr::str_c("<div style='all:initial;'>\n", gt::as_raw_html(x), "\n</div>") %>%
    knitr::asis_output()
}
registerS3method("knit_print", "gt_tbl", knit_print.gt, envir = asNamespace("gt"))
```

```{r}
#| label: create-eia-sheets-list

sheets_923  <- get_sheets("923")
sheets_860  <- get_sheets("860")
sheets_861  <- get_sheets("861")
sheets_860m <- get_sheets("860m")

tab_923  <- make_sheets_table(sheets_923, "923") 
tab_860  <- make_sheets_table(sheets_860, "860")
tab_861  <- make_sheets_table(sheets_861, "861")
tab_860m <- make_sheets_table(sheets_860m, "860m")
 
sheets_used923 <-   c("Page 1 Generation and Fuel Data", # eia-923
                      "Page 1 Puerto Rico",
                      "Page 3 Boiler Fuel Data",
                      "Page 4 Generator Data",
                      "8C Air Emissions Control Info")

sheets_used860 <-  c("Operable",                       # eia-860
                      "Proposed",
                      "Retired and Canceled",
                      "Boiler Generator",
                      "Boiler NOx",
                      "Boiler SO2",
                      "Boiler Mercury",
                      "Boiler Particulate Matter",
                      "Emissions Control Equipment",
                      "Emissions Standards & Strategies",
                      "Boiler Info & Design Parameters",
                      "FGD",
                      "Plant")

sheets_used860m <- c("Operating_PR",
                     "Retired_PR")

sheets_used861 <- c("Balancing Authority",
                    "States")

# file_name_schedule_2_3_4_5_m_12 <- grep("2_3_4_5_M_12", eia_923_files, value = TRUE)


# tab_923 <- style_sheets_table(sheets_used923, tab_923)
# tab_860 <- style_sheets_table(sheets_used860, tab_860)
# tab_860m <- style_sheets_table(sheets_used860m, tab_860m)
# tab_861 <- style_sheets_table(sheets_used861, tab_861)
```

#### EIA Files and Sheets {#eia-files-sheets}

::: panel-tabset
#### Overview

*Click through the tabs above to view files represented from each EIA source.*

**EIA-923**: Data reported on fuel consumption and generation

**EIA-860**: Data reported on electric generators

**EIA-861**: Data collected from distribution utilities and power marketers

**EIA-860m**: Data reported monthly on generating units (used to obtain data for Puerto Rico)

#### EIA-923

```{r}
#| label: print-eia-923-sheets
#| tbl-cap: "EIA-923 sheets"
#| echo: false

tab_923
```

#### EIA-860

```{r}
#| label: print-eia-860-sheets
#| echo: false
#| tbl-cap: "EIA-860 sheets"

tab_860
```

#### EIA-861

```{r}
#| label: print-eia-861-sheets
#| echo: false
#| tbl-cap: "EIA-861 sheets"

tab_861
```

#### EIA-860m

```{r}
#| label: print-eia-860m-sheets
#| echo: false
#| tbl-cap: "EIA-860m sheets"

tab_860m
```
:::

## Load Crosswalks and Static Tables

Crosswalks and static tables are used to supplement EPA and EIA files and provide information on one-off changes, descriptions, emission factors, or overall conversions.

```{r}
#| label: create-xwalk-summary

path <- glue::glue("data/static_tables")

    files <- list.files(path)
    
    # filter for only necessary files
    file_files <- stringr::str_subset(files, ".xls|.xlsx|.csv")
    
# table for crosswalks
tab_xwalk <- 
      tibble(file_files) %>%
      rename("Crosswalks and Static Tables" = file_files) %>%
      gt::gt() %>% 
      gt::tab_style(
        style = cell_text(weight = "bold"),
        locations = cells_row_groups()
      ) %>% 
      gt::tab_style(
        style = cell_text(size = 14, weight = "bold"),
        locations = cells_column_labels()
      ) %>%
      gt::tab_caption(caption = glue::glue("Crosswalks and Static Tables"))
```

::: panel-tabset
#### Overview

*Click on the tab to view crosswalk and static table files*

#### Files

```{r}
#| label: xwalk-summary
#| echo: false

tab_xwalk
```
:::

# Clean Raw Data Files

## EPA

There are several procedures applied to the raw EPA file:

-   Variable name standardization

    -   All variable names are converted to snake case (e.g., "snake_case").

    -   Each form includes identifiers such as a given plant name, prime mover, fuel type, etc., but the assigned column names are inconsistent. To facilitate data operations (e.g., joins) and reduce confusion, we use a common naming scheme across all files (including EIA and EPA).

        -   `plant_id`

        -   `plant_name`

        -   `plant_state`

        -   `prime_mover`

        -   `fuel_type`

        -   `generator_id`

        -   `boiler_id`

        -   `nameplate_capacity`

-   Removing unnecessary plants and columns

    -   Plants listed as future, retired, or long-term cold storage are removed. Additionally, plants with IDs above 80000 are removed

-   Create source variables and apply source: `EPA/CAPD`

    -   `heat_input_source`

    -   `heat_input_oz_source`

    -   `nox_source`

    -   `nox_oz_source`

    -   `so2_source`

    -   `co2_source`

    -   `hg_source`

-   Re-coding values to standardized abbreviations

    -   Ex. Operating Status to OP, unit type description to unit type abbreviation

-   Removing unnecessary notes about start date

    -   This keeps all data rows into a usable, consistent format. In the raw version, some plants have added notes about dates or the plant.

```{r}
#| label: data-clean-epa 
#| file: "scripts/data_clean_epa.R" 
#| results: hold
```

::: panel-tabset
#### Overview

*Click tab above to view variables contained in* `epa_clean.RDS`.

#### EPA clean

```{r}
#| label: create-epa-summary-table 
#| echo: false  

create_summary_table(readr::read_rds(glue::glue("data/clean_data/epa/{params$eGRID_year}/epa_clean.RDS")))
```
:::

## EIA

From the raw Excel downloads, we load, clean, and save select files that are used in eGRID production. Three "clean" EIA files are ultimately created:

-   `eia_923_clean.RDS`

-   `eia_860_clean.RDS`

-   `eia_861_clean.RDS`

Each of these .RDS files contains lists of the relevant tables (stored as dataframes) from each EIA form.

There are several procedures that are applied to each of the raw EIA files:

-   Handling Excel format

    -   Each Excel file contains header rows of varying lengths. These rows are skipped when read in.

    -   Files contain various missing value characters, including: " ","X", and ".". These characters are converted to explicit missing values (i.e., "NA")

-   Variable name standardization

    -   The same method as EPA data above.

```{r}
#| label: data-clean-eia
#| file: "scripts/data_clean_eia.R"
#| results: hold
```

```{r}
#| label: load-eia-clean-files
#| echo: false

eia_923_files <- read_rds(
        glue::glue("data/clean_data/eia/{params$eGRID_year}/eia_923_clean.RDS"))
eia_860_files <- read_rds(
        glue::glue("data/clean_data/eia/{params$eGRID_year}/eia_860_clean.RDS"))
eia_861_files <- read_rds(
        glue::glue("data/clean_data/eia/{params$eGRID_year}/eia_861_clean.RDS"))
```

### EIA-923

::: panel-tabset
#### Overview

*Click through the tabs above to preview values represented from required EIA-923 files.*

```{r}
#| label: eia-923-summary-tabs
#| results: asis

tabs_923 <- 
  eia_923_files %>% 
  map(., ~ create_summary_table(.x))

purrr::iwalk(tabs_923, ~ {
  cat("#### ", .y, "\n\n")
  
  print(.x)
  
  cat("\n\n")
} )
```
:::

### EIA-860

::: panel-tabset
#### Overview

*Click through the tabs above to preview values represented from required EIA-860 files.*

```{r}
#| label: eia-860-summary-tabs
#| echo: false
#| results: false

tabs_860 <- 
  eia_860_files %>% 
  map(., ~ create_summary_table(.x))
```

```{r}
#| label: eia-860-summary-tabs-2
#| echo: false
#| results: asis

purrr::iwalk(tabs_860, ~ {
  cat("#### ", .y, "\n\n")
  
  print(.x)
  
  cat("\n\n")
} )
```
:::

### EIA-861

::: panel-tabset
#### Overview

*Click through the tabs above to preview values represented from required EIA-861 files.*

```{r}
#| label: eia-861-summary-tabs
#| echo: false
#| results: asis

tabs_861 <- 
  eia_861_files %>% 
  map(., ~ create_summary_table(.x))

purrr::iwalk(tabs_861, ~ {
  cat("#### ", .y, "\n\n")
  
  print(.x)
  
  cat("\n\n")
} )
```
:::

# Generator File

The generator file uses data from `eia_860_clean.RDS`, including all operable and retired generators . The code pulls variables from EIA-860 data (`boiler_generator` and `combined`) and counts the number of boilers. Then, we assign generation to each generator value.

Direct generation is assigned to each generator values through the `EIA-923 Generator` file. For values not included in the `EIA-923 Generator` file, generation is determined by using a nameplate capacity ratio with `EIA-923 Generator and Fuel` data. A capacity factor is assigned to each generator.

For full documentation, reference the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

Crosswalks used in this file:

-   `epa_plants_to_delete.csv`

-   `manual_corrections.xlsx`

-   `og_oth_units_to_change_fuel_type.csv`

-   `xwalk_oris_epa.csv`

## Produce Generator File

```{r}
#| label: generator-file-create
#| file: "scripts/generator_file_create.R"
#| results: hold
```

```{r}
#| label: generator-file-table
#| include: false

generator_file <- readr::read_rds(
           glue::glue("data/outputs/{params$eGRID_year}/generator_file.RDS"))
```

## View Generator File Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data contained within the generator file.*

#### Data Summary

```{r}
#| label: gen-file-summary

create_summary_table(generator_file)
```

#### Generation Distributions

```{r}
#| label: gen-file-distributions 
#| fig-height: 10

plot_gen_ann <- 
  generator_file %>% 
  ggplot(aes(x = generation_ann)) + 
  geom_histogram() +
  theme_minimal() +
  labs(title = "Annual Generation")

plot_gen_oz <-
  generator_file %>% 
  ggplot(aes(x = generation_oz)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Ozone Months Generation")

plot_gen_ann_source <-
  generator_file %>%
  ggplot(aes(x = gen_data_source, y = generation_ann)) +
  geom_boxplot() +
  theme_minimal() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  labs(title = "Annual Generation by Data Source")

  (plot_gen_ann + plot_gen_oz) / plot_gen_ann_source
```

#### Distribution of Data Sources

```{r}
#| label: generator-file-data-source-dists

generator_file %>% 
  count(gen_data_source) %>% 
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = gen_data_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Generation Data Sources",
    y = "Share of generators",
    x = NULL
  )
```
:::

# Unit File

The unit file data includes grid connected units from EPA/CAPD data, unique EIA-923 boilers, unique EIA-860 generators.

The unit file includes heat input and emissions values for each unit included where data is available.

For full documentation, reference the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

Crosswalks used in this file:

-   `biomass_units_to_add_to_unit_file.csv`

-   `co2_ch4_n2o_ef.csv`

-   `emission_factors.csv`

-   `epa_plants_to_delete.csv`

-   `fuel_type_categories.csv`

-   `geothermal_emission_factors.csv`

-   `manual_corrections.xlsx`

-   `nrel_geothermal_table.csv`

-   `og_oth_units_to_change_fuel_type.csv`

-   `units_to_remove.csv`

-   `xwalk_860_boiler_control_id.csv`

-   `xwalk_boiler_firing_type.csv`

-   `xwalk_epa_eia_power_sector.csv`

-   `xwalk_oris_epa.csv`

-   `xwalk_pr_oris.csv`

## Produce Unit File

```{r}
#| label: unit-file-create
#| file: "scripts/unit_file_create.R"
#| results: hold
```

```{r}
#| label: unit-file-table
#| include: false

unit_file <- readr::read_rds(
           glue::glue("data/outputs/{params$eGRID_year}/unit_file.RDS"))
```

## View Unit File Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data contained within the unit file.*

#### Data Summary

```{r}
#| label: unit-file-summary

create_summary_table(unit_file)
```

#### Heat Input Distributions

```{r}
#| label: unit-file-heat-in-dist
#| fig-height: 10

plot_unt_heat_in <-
  unit_file %>%
  ggplot(aes(x = heat_input)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Heat Input")

plot_unt_heat_in_oz <-   
  unit_file %>%
  ggplot(aes(x = heat_input_oz)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Heat Input Ozone")

plot_unt_heat_in_source_dist <-
  unit_file %>%
  count(heat_input_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = heat_input_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Heat Input Data Sources",
    y = "Share of units",
    x = NULL
    )

plot_unt_heat_in_oz_source_dist <-
  unit_file %>%
  count(heat_input_oz_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = heat_input_oz_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Heat Input Ozone Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_unt_heat_in + plot_unt_heat_in_oz) / plot_unt_heat_in_source_dist / plot_unt_heat_in_oz_source_dist
```

#### NOx Distributions

```{r}
#| label: unit-file-nox-dist
#| fig-height: 10

plot_unt_nox <-
  unit_file %>%
  ggplot(aes(x = nox_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "NOx Mass")

plot_unt_nox_oz <-   
  unit_file %>%
  ggplot(aes(x = nox_oz_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "NOx Mass Ozone")

plot_unt_nox_sources_dist <-
  unit_file %>%
  count(nox_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = nox_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of NOx Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

plot_unt_nox_oz_source_dist <-
  unit_file %>%
  count(nox_oz_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = nox_oz_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of NOx Mass Ozone Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_unt_nox + plot_unt_nox_oz) / (plot_unt_nox_sources_dist) / (plot_unt_nox_oz_source_dist)
```

#### SO2 Distributions

```{r}
#| label: unit-file-so2-dist
#| fig-height: 10

plot_unt_so2 <-
  unit_file %>%
  ggplot(aes(x = so2_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "SO2 Mass")

plot_unt_so2_sources_dist <-
  unit_file %>%
  count(so2_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = so2_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of SO2 Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

plot_unt_so2 / plot_unt_so2_sources_dist
```

#### CO2 Distributions

```{r}
#| label: unit-file-co2-dist
#| fig-height: 10

plot_unt_co2 <-
  unit_file %>%
  ggplot(aes(x = co2_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "SO2 Mass")

plot_unt_co2_sources_dist <-
  unit_file %>%
  count(co2_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = co2_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of CO2 Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

plot_unt_co2 / plot_unt_co2_sources_dist
```
:::

# Plant File

The plant file combines EIA form data, `EIA-860`, `EIA-861`, and `EIA-923`, with the outputs of the previous two files: `generator_file.RDS` and `unit_file.RDS`.

The plant file calculates unadjusted and adjusted heat input and emissions, generation (total and by fuel type), emission rates, and resource mixes for each plant.

Adjusted heat input and emission values account for combined heat and power (CHP) and biomass facilities. The plant file also reports CHP and biomass specific heat input and emissions values.

For full documentation, reference the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

Crosswalks used in this file:

-   `ba_codes.csv`

-   `chp_database.csv`

-   `co2_ch4_n2o_ef.csv`

-   `egrid_2022_chp.csv`

-   `egrid_nerc_subregions.csv`

-   `fuel_type_categories.csv`

-   `global_warming_potential.csv`

-   `manual_corrections.xlsx`

-   `nerc_assessment_areas_grouped_by_plant.csv`

-   `og_oth_units_to_change_fuel_type.csv`

-   `state_county_fips.csv`

-   `xwalk_alaska_fips.csv`

-   `xwalk_balancing_authority.csv`

-   `xwalk_fips_names_update.csv`

-   `xwalk_nerc_assessment.csv`

-   `xwalk_oris_epa.csv`

-   `xwalk_oris_subregion.csv`

-   `xwalk_subregion_transmission.csv`

-   `xwalk_subregion_utility.csv`

## Produce Plant File

```{r}
#| label: plant-file-create
#| file: "scripts/plant_file_create.R"
#| results: hold
```

```{r}
#| label: plant-file-table
#| include: false

plant_file <- readr::read_rds(
           glue::glue("data/outputs/{params$eGRID_year}/plant_file.RDS"))
```

## View Plant File Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data contained within the plant file.*

#### Data Summary

```{r}
#| label: plant-file-summary

create_summary_table(plant_file)
```

#### Heat Input Distributions

```{r}
#| label: plant-file-heat-in-dist
#| fig-height: 10

plot_plnt_heat_in <-
  plant_file %>%
  ggplot(aes(x = heat_input)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Heat Input")

plot_plnt_unadj_heat_in <-
  plant_file %>%
  ggplot(aes(x = unadj_heat_input)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted Heat Input")

plot_plnt_heat_in_dist <-
  plant_file %>%
  count(unadj_heat_input_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_heat_input_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. Heat Input Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_heat_in + plot_plnt_unadj_heat_in) / plot_plnt_heat_in_dist
```

#### Heat Input Ozone Distributions

```{r}
#| label: plant-file-heat-in-oz-dist
#| fig-height: 10

plot_plnt_heat_in_oz <-
  plant_file %>%
  ggplot(aes(x = heat_input_oz)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Heat Input Ozone")

plot_plnt_unadj_heat_in_oz <-
  plant_file %>%
  ggplot(aes(x = unadj_heat_input_oz)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted Heat Input Ozone")

plot_plnt_heat_in_oz_dist <-
  plant_file %>%
  count(unadj_heat_input_oz_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_heat_input_oz_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. Heat Input Ozone Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_heat_in_oz + plot_plnt_unadj_heat_in_oz) / plot_plnt_heat_in_oz_dist
```

#### NOx Distributions

```{r}
#| label: plant-file-nox-dist
#| fig-height: 10

plot_plnt_nox <-
  plant_file %>%
  ggplot(aes(x = nox_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "NOx Mass")

plot_plnt_unadj_nox <-
  plant_file %>%
  ggplot(aes(x = unadj_nox_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted NOx Mass")

plot_plnt_nox_rate <-
  plant_file %>%
  ggplot(aes(x = nox_out_emission_rate)) +
  geom_histogram() +
  theme_minimal() +
  xlim(c(0, 150)) + # adding in limit to deal with outliers
  labs(title = "NOx Emission Output Rate")

plot_plnt_nox_dist <-
  plant_file %>%
  count(unadj_nox_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_nox_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. NOx Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_nox + plot_plnt_unadj_nox) / plot_plnt_nox_rate / plot_plnt_nox_dist
```

#### NOx Ozone Distributions

```{r}
#| label: plant-file-nox-oz-dist
#| fig-height: 10

plot_plnt_nox_oz <-
  plant_file %>%
  ggplot(aes(x = nox_oz_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "NOx Mass Ozone")

plot_plnt_unadj_nox_oz <-
  plant_file %>%
  ggplot(aes(x = unadj_nox_oz_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted NOx Mass Ozone")

plot_plnt_nox_oz_rate <-
  plant_file %>%
  ggplot(aes(x = nox_oz_out_emission_rate)) +
  geom_histogram() +
  theme_minimal() +
  xlim(c(0, 150)) + # adding in limit to deal with outliers
  labs(title = "NOx Ozone Emission Output Rate")

plot_plnt_nox_oz_dist <-
  plant_file %>%
  count(unadj_nox_oz_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_nox_oz_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. NOx Ozone Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_nox_oz + plot_plnt_unadj_nox_oz) / plot_plnt_nox_oz_rate / plot_plnt_nox_oz_dist
```

#### SO2 Distributions

```{r}
#| label: plant-file-so2-dist
#| fig-height: 10

plot_plnt_so2 <-
  plant_file %>%
  ggplot(aes(x = so2_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "SO2 Mass")

plot_plnt_unadj_so2 <-
  plant_file %>%
  ggplot(aes(x = unadj_so2_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted SO2 Mass")

plot_plnt_so2_rate <-
  plant_file %>%
  ggplot(aes(x = so2_out_emission_rate)) +
  geom_histogram() +
  theme_minimal() +
  xlim(c(0, 50)) + # adding in limit to deal with outliers
  labs(title = "SO2 Emission Output Rate")

plot_plnt_so2_dist <-
  plant_file %>%
  count(unadj_so2_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_so2_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. SO2 Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_so2 + plot_plnt_unadj_so2) / plot_plnt_so2_rate / plot_plnt_so2_dist
```

#### CO2 Distributions

```{r}
#| label: plant-file-co2-dist
#| fig-height: 10

plot_plnt_co2 <-
  plant_file %>%
  ggplot(aes(x = co2_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "CO2 Mass")

plot_plnt_unadj_co2 <-
  plant_file %>%
  ggplot(aes(x = unadj_co2_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted CO2 Mass")

plot_plnt_co2_rate <-
  plant_file %>%
  ggplot(aes(x = co2_out_emission_rate)) +
  geom_histogram() +
  theme_minimal() +
  xlim(c(0, 30000)) + # adding in limit to deal with outliers
  labs(title = "CO2 Emission Output Rate")

plot_plnt_co2_dist <-
  plant_file %>%
  count(unadj_co2_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_co2_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. CO2 Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_co2 + plot_plnt_unadj_co2) / plot_plnt_co2_rate / plot_plnt_co2_dist
```

#### CH4 Distributions

```{r}
#| label: plant-file-ch4-dist
#| fig-height: 10

plot_plnt_ch4 <-
  plant_file %>%
  ggplot(aes(x = ch4_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "CH4 Mass")

plot_plnt_unadj_ch4 <-
  plant_file %>%
  ggplot(aes(x = unadj_ch4_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted CH4 Mass")

plot_plnt_ch4_rate <-
  plant_file %>%
  ggplot(aes(x = ch4_out_emission_rate)) +
  geom_histogram() +
  theme_minimal() +
  xlim(c(0, 10)) + # adding in limit to deal with outliers
  labs(title = "CH4 Emission Output Rate")

plot_plnt_ch4_dist <-
  plant_file %>%
  count(unadj_ch4_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_ch4_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. CH4 Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_ch4 + plot_plnt_unadj_ch4) / plot_plnt_ch4_rate / plot_plnt_ch4_dist
```

#### N2O Distributions

```{r}
#| label: plant-file-n2o-dist
#| fig-height: 10

plot_plnt_n2o <-
  plant_file %>%
  ggplot(aes(x = n2o_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "N2O Mass")

plot_plnt_unadj_n2o <-
  plant_file %>%
  ggplot(aes(x = unadj_n2o_mass)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Unadjusted N2O Mass")

plot_plnt_n2o_rate <-
  plant_file %>%
  ggplot(aes(x = n2o_out_emission_rate)) +
  geom_histogram() +
  theme_minimal() +
  xlim(c(0, 1)) + # adding in limit to deal with outliers
  labs(title = "N2O Emission Output Rate")

plot_plnt_n2o_dist <-
  plant_file %>%
  count(unadj_n2o_source) %>%
  mutate(proportion = n/sum(n)) %>%
  ggplot(aes(x = unadj_n2o_source, y = proportion)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = scales::wrap_format(30)) +
  scale_y_continuous(labels = scales::label_percent()) +
  geom_text(aes(label = scales::percent(proportion)),
            nudge_y = .05) +
  theme_minimal() +
  labs(
    title = "Distribution of Unadj. N2O Mass Data Sources",
    y = "Share of units",
    x = NULL
    )

(plot_plnt_n2o + plot_plnt_unadj_n2o) / plot_plnt_n2o_rate / plot_plnt_n2o_dist
```
:::

# Region Aggregation

The plant file (`plant_file.RDS`) is aggregated to calculate the heat input, emissions, generation, fuel-based net generation, resource mix, and nameplate capacity from the plant-level data to the various aggregated levels: state (ST), balancing authority (BA), eGRID subregion (SRL), NERC region (NRL), and US level.

The aggregated files also calculate region specific output, input, combustion output, fuel-specific output, fuel-specific input, and nonbaseload output emissions rates. The aggregated level resource mix is estimated based on the summed generation by fuel values from the plant file. The nonbaseload generation is estimated by fuel type and resource mix.

For full documentation, reference the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

Crosswalks used in this file:

-   `nerc_region_names.csv`

## Produce Aggregation Files

```{r}
#| label: region-aggregation-create
#| file: "scripts/region_aggregation_create.R"
#| results: hold
```

```{r}
#| label: load-reg-agg-files
#| echo: false

ba_agg  <- read_rds(
        glue::glue("data/outputs/{params$eGRID_year}/ba_aggregation.RDS"))
st_agg  <- read_rds(
        glue::glue("data/outputs/{params$eGRID_year}/state_aggregation.RDS"))
srl_agg <- read_rds(
        glue::glue("data/outputs/{params$eGRID_year}/subregion_aggregation.RDS"))
nrl_agg <- read_rds(
        glue::glue("data/outputs/{params$eGRID_year}/nerc_aggregation.RDS"))
us_agg  <- read_rds(
        glue::glue("data/outputs/{params$eGRID_year}/us_aggregation.RDS"))
```

## View Aggregation Files Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data for each region aggregation.*

**BA**: Balancing Authority Aggregation

**ST**: State Aggregation

**SRL**: Subregion Aggregation

**NRL**: NERC Region Aggregation

**US**: U.S. Aggregation

#### BA

```{r}
#| label: ba-agg-summary

create_summary_table(ba_agg)
```

#### ST

```{r}
#| label: st-agg-summary

create_summary_table(st_agg)
```

#### SRL

```{r}
#| label: srl-agg-summary

create_summary_table(srl_agg)
```

#### NRL

```{r}
#| label: nrl-agg-summary

create_summary_table(nrl_agg)
```

#### US

```{r}
#| label: us-agg-summary

create_summary_table(us_agg)
```
:::

# Grid Gross Loss File

Grid gross loss (GGL) is calculated using EIA's State Electricity Profiles: `Table 10: Supply and disposition of energy`.

For full documentation, reference the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

Crosswalk used in this file:

-   `state_and_interconnection.csv`

-   `nerc_region_and_interconnect.xlsx`

## Produce Grid Gross Loss File

```{r}
#| label: grid-gross-loss-create
#| file: "scripts/grid_gross_loss_create.R"
#| results: hold
```

```{r}
#| label: ggl-file-table
#| include: false

ggl_file <- readr::read_rds(
           glue::glue("data/outputs/{params$eGRID_year}/grid_gross_loss.RDS"))
```

## View Grid Gross Loss File Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data contained within the grid gross loss (GGL) file.*

#### Data Summary

```{r}
#| label: ggl-file-summary

create_summary_table(ggl_file)
```

#### View Plots

```{r}
#| label: ggl-file-plots

ggl_plot <- ggl_file %>%
              ggplot(aes(x = interconnect, y = ggl*100)) +
              geom_bar(stat="identity") +
              geom_text(aes(label = sprintf("%.1f%%", ggl*100)), vjust = +1.5, colour = "white") + 
              theme_minimal() +
              labs(
                title = "Grid Gross Loss",
                y = "Percentage",
                x = "Interconnect"
                )

est_losses_plot <- ggl_file %>%
                    ggplot(aes(x = interconnect, y = est_losses_sum)) +
                    geom_bar(stat="identity") +
                    #geom_text(aes(label = sprintf("%.2f", est_losses_sum)), vjust = -0.5) + 
                    theme_minimal() +
                    theme(
                      axis.text.x = element_text(angle = 45, hjust = 1)
                    ) +
                    labs(
                      title = "Estimated Losses",
                      y = "MWh",
                      x = "Interconnect"
                      )

tot_disp_sub_ex_plot <- ggl_file %>%
                          ggplot(aes(x = interconnect, y = tot_disp_sub_ex_sum)) +
                          geom_bar(stat = "identity") +
                          #geom_text(aes(label = sprintf("%.2f", tot_disp_sub_ex_sum)), vjust = -0.5) + 
                          theme_minimal() +
                          theme(
                            axis.text.x = element_text(angle = 45, hjust = 1)
                           ) +
                          labs(
                            title = "Total Disposition - Exports",
                            y = "MWh",
                            x = "Interconnect"
                            )


direct_use_plot <- ggl_file %>%
                    ggplot(aes(x = interconnect, y = direct_use_sum)) +
                    # geom_text(aes(label = sprintf("%.2f", direct_use_sum)), vjust = -0.5) + 
                    geom_bar(stat = "identity") +
                    theme_minimal() +
                    theme(
                      axis.text.x = element_text(angle = 45, hjust = 1)
                    ) +
                    labs(
                      title = "Direct Use",
                      y = "MWh",
                      x = "Interconnect"
                      )


(ggl_plot) / (est_losses_plot + tot_disp_sub_ex_plot + direct_use_plot) + plot_layout(heights = c(2,1))
```
:::

# Demographics File

The demographics file identifies the demographic characteristics of surrounding neighborhoods within a 3-mile radius for each plant. The demographic data is obtained from EPA's EJScreen API data and lat/lon coordinates of each plant. For more information on the EJScreen data, [see EJScreen's methodology](https://www.epa.gov/ejscreen/technical-information-and-data-downloads).

For full documentation, reference the [eGRID Technical Guide](https://www.epa.gov/egrid/egrid-technical-guide).

## Produce Demographics File

```{r}
#| label: demographics-file-create
#| results: hold

if (params$run_demo_file) {

    source("scripts/demographics_file_create.R")
    print("demographics_file_create is running because run_script is TRUE. Code will take 4-5 hours to complete.")

} else {

    print("Skipping demographics_file_create.R because run_demo_file is FALSE.")

}
```

# Metric Conversion File

The metric file script produces a metric version of the eGRID datasets by converting certain data from imperial to metric units. The results are the following metric version files:

-   `generator_file_metric`

-   `unit_file_metric`

-   `plant_file_metric`

-   `state_aggregation_metric`

-   `ba_aggregation_metric`

-   `subregion_aggregation_metric`

-   `nerc_aggregation_metric`

-   `us_aggregation_metric`

-   `grid_gross_loss_metric`

The eGRID variables added or altered in the metric file versions are included in the `metric_structure.xlsx` document while the conversion rates between imperial and metric units are listed in `conversion_factors.csv` as shown below.

## Conversion Table

```{r}
#| label: conversion-table

conversion_table <- read_csv("data/static_tables/conversion_factors.csv")


conversion_table %>%
      gt::gt() %>%
      gt::cols_label(
          from = gt::md("**Imperial**"),
          to = gt::md("**Metric**"),
          conversion = gt::md("**Conversion Factor**")
      )
```

## Produce Metric Version Files

```{r}
#| label: metric-files-create
#| file: "scripts/metric_files_create.R"
#| results: hold
```

# Final Formatting

The data is formatted into an Excel file that contains all eight levels of data aggregation. For headers, we add descriptions and label conventions to maintain consistency with previous eGRID releases. Formatting is applied for both imperial unit version and the metric unit version.

## Produce Final eGRID Documents

### Imperial Version

The final output file is `r glue::glue("egrid{params$eGRID_year}_data.xlsx")`.

```{r}
#| label: final-formatting
#| file: "scripts/final_formatting.R"
#| results: hold
```

### Metric Version

The final metric output file is `r glue::glue("egrid{params$eGRID_year}_data_metric.xlsx")`.

```{r}
#| label: metric-final-formatting
#| file: "scripts/final_formatting_metric.R"
#| results: hold
```

# eGRID Summary

## Summary Tables

A summary tables document is produced to provide a synopsis of the eGRID information across states and eGRID subregions. The summary tables are saved as `summary_tables.xlsx`.

### Produce Summary Tables

```{r}
#| label: summary-tables-create
#| file: "scripts/summary_tables_create.R"
#| results: false
```

### Summary Tables Data

Below are the names of the summary tables included in the document.

```{r}
#| label: summary-tables-list
#| echo: false

kbl(names(table_data), col.names = "Summary Table Names") %>%
  kable_styling()
```

## Number of Records

The following lines outputs the number of records for contained within each level of aggregation.

```{r}
#| label: egrid-summary
#| results: hold

print(glue::glue("Generator (GEN) Records: {nrow(generator_file)}"))
print(glue::glue("Unit (UNIT) Records: {nrow(unit_file)}"))
print(glue::glue("Plant (PLNT) Records: {nrow(plant_file)}"))
print(glue::glue("State (ST) Records: {nrow(st_agg)}"))
print(glue::glue("Balancing Authority (BA) Records: {nrow(ba_agg)}"))
print(glue::glue("eGRID Subregion (SRL) Records: {nrow(srl_agg)}"))
print(glue::glue("NERC Region (NRL) Records: {nrow(nrl_agg)}"))
print(glue::glue("US (US) Records: {nrow(us_agg)}"))
```
