---
title: "Monthly Production Model QA"
format: html
editor: source
table-of-contents: true
---

```{r}
#| label: load-libraries
#| echo: false
#| message: false

library(dplyr)
library(ggplot2)
library(kableExtra)
library(readr)
library(tidyr)
library(patchwork)
library(stringr)

```

```{r}
#| label: load-functions
#| echo: false
#| message: false

source("scripts/qa/monthly_qa/function_plot_monthly_comparison.R")
base::load("data/static_tables/name_matches.RData")
```

```{r}
#| label: read-format-data
#| echo: false
#| message: false

# load in unit data, format, and merge
unit_monthly <- 
  read_rds("data/outputs/2023/unit_file_monthly.RDS")

colnames(unit_monthly) <- paste0(colnames(unit_monthly), "_monthly")
unit_monthly <- unit_monthly %>% 
  rename("plant_id" = "plant_id_monthly",
         "unit_id" = "unit_id_monthly", 
         "prime_mover" = "prime_mover_monthly",
         "year" = "year_monthly",
         "month" = "month_monthly") %>% 
  mutate(month = as.character(month))

unit_annual <- 
  read_rds("data/outputs/2023/unit_file.RDS")

colnames(unit_annual) <- paste0(colnames(unit_annual), "_annual")
unit_annual <- unit_annual %>% 
  rename("plant_id" = "plant_id_annual",
         "unit_id" = "unit_id_annual", 
         "prime_mover" = "prime_mover_annual",  
         "year" = "year_annual") %>% 
  mutate(month = "annual")

# load in generator data, format, and merge
generator_monthly <- 
  read_rds("data/outputs/2023/generator_file_monthly.RDS")

colnames(generator_monthly) <- paste0(colnames(generator_monthly), "_monthly")
generator_monthly <- generator_monthly %>% 
  rename("plant_id" = "plant_id_monthly",
         "generator_id" = "generator_id_monthly", 
         "prime_mover" = "prime_mover_monthly",
         "year" = "year_monthly",
         "month" = "month_monthly") %>% 
  mutate(month = as.character(month))

generator_annual <- 
  read_rds("data/outputs/2023/generator_file.RDS")

colnames(generator_annual) <- paste0(colnames(generator_annual), "_annual")
generator_annual <- generator_annual %>% 
  rename("plant_id" = "plant_id_annual",
         "generator_id" = "generator_id_annual", 
         "prime_mover" = "prime_mover_annual",  
         "generation_annual" = "generation_ann_annual",
         "year" = "year_annual") %>% 
  mutate(month = "annual")

# load in plant data, format, and merge
plant_monthly <- 
  read_rds("data/outputs/2023/plant_file_monthly.RDS") %>% 
  mutate(month = as.character(month))

plant_monthly_2 <- plant_monthly
colnames(plant_monthly_2) <- paste0(colnames(plant_monthly_2), "_monthly")
plant_monthly_2 <- 
  plant_monthly_2 %>% 
  rename("plant_id" = "plant_id_monthly",
         "year" = "year_monthly",
         "month" = "month_monthly") %>% 
  mutate(month = as.character(month))

plant_annual <- 
  read_rds("data/outputs/2023/plant_file.RDS") 

# rename to new version of column names
new_vars <- 
  plant_nonmetric_annual
colnames(plant_annual) <- new_vars
  
plant_annual_2 <- plant_annual
colnames(plant_annual_2) <- paste0(colnames(plant_annual_2), "_annual")
plant_annual_2 <- 
  plant_annual_2 %>% 
  rename("plant_id" = "plant_id_annual",
         "year" = "year_annual") 

plant_merged <-
  plant_monthly %>% 
  full_join(plant_annual %>% mutate(month = "annual"))

plant_merged$month <- factor(plant_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

```

## Unit file comparison

The differences between the totals of heat input and emission masses of the monthly and annual unit files are shown here. The monthly version is aggregated to the annual resolution to compare.

In the tabset below, we list what units have a difference greater than 0.01 for heat input and emission masses. We note which units are ozone reporters, since the methodology for filling non-ozone months is different between annual (non-ozone distributed) and monthly (non-ozone filled via EIA and summed to annual) versions for heat input and annual NOx mass. We also note the respondent frequency of units in EIA, since Annual reporters under the monthly version have heat input filled from EIA-923 Generation and Fuel. 

```{r}
#| label: unit-comparison
#| echo: false
#| message: false

# read in EPA data to identify OS reporters
epa <- 
  read_rds("data/clean_data/epa/2023/epa_clean_annual.RDS") %>% 
  select(plant_id, unit_id, reporting_frequency) %>% 
  distinct()

# read in EIA data to identify Annual reporters (which may not represent monthly version well)
eia_923 <- 
  read_rds("data/clean_data/eia/2023/eia_923_clean.RDS") 

annual_reporters <-
  eia_923$boiler_fuel_data %>% 
  select(plant_id, boiler_id, prime_mover, respondent_frequency) %>% 
  distinct() %>% 
  group_by(plant_id, boiler_id, prime_mover) %>% 
  summarize(respondent_frequency = paste(respondent_frequency, collapse = ", ")) %>% 
  ungroup()

# sum monthly version to annual values
unit_monthly_sum <- 
  unit_monthly %>% 
  group_by(plant_id, unit_id, prime_mover) %>% 
  summarize(heat_input_monthly = sum(heat_input_monthly, na.rm = TRUE), 
            nox_mass_monthly = sum(nox_mass_monthly, na.rm = TRUE), 
            so2_mass_monthly = sum(so2_mass_monthly, na.rm = TRUE), 
            co2_mass_monthly = sum(co2_mass_monthly, na.rm = TRUE)) %>% 
  ungroup()

# total monthly version 
unit_total_monthly_sum <- 
  unit_monthly_sum %>% 
  summarize(heat_input = sum(heat_input_monthly, na.rm = TRUE), 
            nox_mass = sum(nox_mass_monthly, na.rm = TRUE),
            so2_mass = sum(so2_mass_monthly, na.rm = TRUE), 
            co2_mass = sum(co2_mass_monthly, na.rm = TRUE)) %>% 
  mutate(agg = "monthly") 

# total annual version to totals
unit_total_annual_sum <- 
  unit_annual %>% 
  summarize(heat_input = sum(heat_input_annual, na.rm = TRUE), 
            nox_mass = sum(nox_mass_annual, na.rm = TRUE), 
            so2_mass = sum(so2_mass_annual, na.rm = TRUE), 
            co2_mass = sum(co2_mass_annual, na.rm = TRUE)) %>% 
  mutate(agg = "annual") 

# calculate difference of total values
unit_total_sum_comp <- 
  rbind(unit_total_monthly_sum, 
        unit_total_annual_sum) %>% 
  relocate(agg) %>% 
  pivot_longer(-c(agg), names_to = "column", values_to = "value") %>% 
  arrange(column) %>% 
  group_by(column) %>% 
  mutate(difference = value - lag(value)) %>% 
  ungroup() %>% 
  mutate(percent_diff = difference / value * 100) 

# produce tale of differences of total values
knitr::kable(unit_total_sum_comp,
             digits = c(0, 0, 0, 0, 2), 
             format.args = list(big.mark = ","), 
             col.names = gsub("[_]", " ", names(unit_total_sum_comp)), 
             caption = "Unit file totals comparison") 

# calculate differences at the unit level
check_unit_diff <- 
  unit_annual %>% 
  full_join(unit_monthly_sum, by = c("plant_id", "unit_id", "prime_mover")) %>% 
  mutate(heat_input_diff = abs(heat_input_annual - heat_input_monthly), 
         heat_input_pct_diff = abs(heat_input_diff / heat_input_monthly) * 100,
         nox_diff = abs(nox_mass_annual - nox_mass_monthly),
         nox_pct_diff = abs(nox_diff / nox_mass_monthly) * 100,
         so2_diff = abs(so2_mass_annual - so2_mass_monthly), 
         so2_pct_diff = abs(so2_diff / so2_mass_monthly) * 100,
         co2_diff = abs(co2_mass_annual - co2_mass_monthly),
         co2_pct_diff = abs(co2_diff / co2_mass_monthly) * 100) %>% 
  left_join(epa, by = c("plant_id", "unit_id")) %>% 
  left_join(annual_reporters, by = c("plant_id", "unit_id" = "boiler_id", "prime_mover"))
```

::: panel-tabset
### Heat input

```{r}
#| label: heat-input-unit-comp
#| echo: false
#| message: false

unit_heat_input_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         heat_input_annual,
         heat_input_monthly,
         heat_input_diff,
         heat_input_pct_diff,
         reporting_frequency,
         respondent_frequency) %>% 
   filter(heat_input_diff > 0.01) %>% 
   arrange(-heat_input_pct_diff)

print(glue::glue("Heat Input Differences > 0.01: {nrow(unit_heat_input_check)}"))
```

Notes:

-   Some differences are attributable to differences in EIA Annual reporters, this needs to be addressed.

-   Some differences are attributable to differences in ozone methodology.

-   Some differences are from EIA-923 Boilers where we updated the EIA Boiler file to sum boilers (and ignore NAs, which updated some heat input to be positive values here and not filled during the NA heat input steps). This applies to about 60 units and are likely the monthly reporters in the list. Teagan has a list of what units were affected. 

```{r}
#| label: heat-input-unit-table
#| echo: false
#| message: false

knitr::kable(unit_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "Heat Input Annual",
                           "Heat Input Monthly",
                           "Heat Input Diff",
                           "Percent Diff",
                           "EPA Reporting Frequency", 
                           "EIA Respondent Frequency"), 
             caption = "Unit file heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### NOx mass

```{r}
#| label: nox-unit-comp
#| echo: false
#| message: false

unit_nox_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         nox_mass_annual,
         nox_mass_monthly,
         nox_diff,
         nox_pct_diff,
         reporting_frequency,
         respondent_frequency) %>% 
   filter(nox_diff > 0.01) %>% 
   arrange(-nox_pct_diff)

print(glue::glue("NOx mass differences > 0.01: {nrow(unit_nox_check)}"))
```

Notes:

-   Some differences are attributable to differences in EIA Annual reporters, this needs to be addressed. 

-   Some differences are attributable to differences in ozone methodology.

-   Plant 54950 missing matching NOx EF factor for DFO, CT unit. 

-   Some differences are due to the monthly version using ozone NOx rates for ozone season months, and annual NOx rates for all other months. 

```{r}
#| label: nox-unit-table
#| echo: false
#| message: false

knitr::kable(unit_nox_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "NOx Mass Annual", 
                           "NOx Mass Monthly", 
                           "Annual NOx Diff",
                           "Percent Diff",
                           "EPA Reporting Frequency",
                           "EIA Respondent Frequency"), 
             caption = "Unit file NOx mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```

### SO2 mass

```{r}
#| label: so2-unit-comp
#| echo: false
#| message: false

unit_so2_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         so2_mass_annual,
         so2_mass_monthly,
         so2_diff,
         so2_pct_diff,
         reporting_frequency,
         respondent_frequency) %>% 
  filter(so2_diff > 0.01) %>% 
  arrange(-so2_pct_diff)

print(glue::glue("SO2 mass differences > 0.01: {nrow(unit_so2_check)}"))
```

Notes:

-   Some differences are due to differences across sulfur content since annual is an average of all monthly sulfur contents, but we use monthly level sulfur contents for the monthly version.

-   15 differences attributable to differences in ozone season methodology.

-   Some differences are attributable to differences in EIA Annual reporters, this needs to be addressed. 

```{r}
#| label: so2-unit-table
#| echo: false
#| message: false

knitr::kable(unit_so2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "SO2 Mass Annual", 
                           "SO2 Mass Monthly", 
                           "Annual SO2 Diff",
                           "Percent Diff",
                           "EPA Reporting Frequency", 
                           "EIA Respondent Frequency"), 
             caption = "Unit file SO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```

### CO2 mass

```{r}
#| label: co2-unit-comp
#| echo: false
#| message: false

unit_co2_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         co2_mass_annual, 
         co2_mass_monthly, 
         co2_diff,
         co2_pct_diff,
         reporting_frequency, 
         respondent_frequency) %>% 
  filter(co2_diff > 0.01) %>% 
  arrange(-co2_pct_diff) 

print(glue::glue("CO2 mass differences > 0.01: {nrow(unit_co2_check)}"))
```

Notes:

-   21 unit differences attributable to differences in ozone season methodology differences.

-   Some differences are attributable to differences in EIA Annual reporters, this needs to be addressed. 

```{r}
#| label: co2-unit-table
#| echo: false
#| message: false

knitr::kable(unit_co2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "CO2 Mass Annual", 
                           "CO2 Mass Monthly", 
                           "Annual CO2 Diff",
                           "Percent Diff", 
                           "EPA Reporting Frequency",
                           "EIA Respondent Frequency"), 
             caption = "Unit file CO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```
:::


## Generator file comparison

The differences between the totals of generation of the monthly and annual unit files are shown here. The monthly version is aggregated to the annual resolution to compare.

In the tabset below, we list what units have a difference greater than 0.01 for generation. We also note which units are ozone reporters, since the methodology for filling non-ozone months is different between annual (non-ozone distributed) and monthly (non-ozone filled via EIA and summed to annual) versions for heat input and annual NOx mass. [flag to correct for generator file information]

```{r}
#| label: generator-comparison
#| echo: false
#| message: false

# read in EPA data to identify OS reporters
# epa <- 
#   read_rds("data/clean_data/epa/2023/epa_clean_annual.RDS") %>% 
#   select(plant_id, unit_id, reporting_frequency) %>% 
#   distinct()

# read in EIA data to identify Annual reporters (which may not represent monthly version well)
eia_923 <- 
  read_rds("data/clean_data/eia/2023/eia_923_clean.RDS") 

annual_reporters <-
  eia_923$boiler_fuel_data %>% 
  select(plant_id, boiler_id, prime_mover, respondent_frequency) %>% 
  distinct() %>% 
  group_by(plant_id, boiler_id, prime_mover) %>% 
  summarize(respondent_frequency = paste(respondent_frequency, collapse = ", ")) %>% 
  ungroup()

# sum monthly version to annual values
generator_monthly_sum <- 
  generator_monthly %>% 
  group_by(year, plant_id, generator_id, prime_mover) %>% 
  summarize(generation_monthly = sum(generation_monthly, na.rm = TRUE)) %>% 
  ungroup()

# total monthly version 
generator_total_monthly_sum <- 
  generator_monthly_sum %>% 
  summarize(generation = sum(generation_monthly, na.rm = TRUE)
            ) %>% 
  mutate(agg = "monthly") 

# total annual version to totals
generator_total_annual_sum <- 
  generator_annual %>% 
  summarize(generation = sum(generation_annual, na.rm = TRUE)) %>% 
  mutate(agg = "annual") 

# calculate difference of total values
generator_total_sum_comp <- 
  rbind(generator_total_monthly_sum, 
        generator_total_annual_sum) %>% 
  relocate(agg) %>% 
  pivot_longer(-c(agg), names_to = "column", values_to = "value") %>% 
  arrange(column) %>% 
  group_by(column) %>% 
  mutate(difference = value - lag(value)) 

# produce tale of differences of total values
knitr::kable(generator_total_sum_comp,
             digits = 0, 
             format.args = list(big.mark = ","), 
             col.names = gsub("[_]", " ", names(generator_total_sum_comp)), 
             caption = "Generator file totals comparison") 

# calculate differences at the unit level
check_generation_diff <- 
  generator_annual %>% 
  full_join(generator_monthly_sum, by = c("plant_id", "generator_id", "prime_mover")) %>% 
  mutate(generation_diff = abs(generation_annual - generation_monthly), 
         generation_pct_diff = abs(generation_diff / generation_monthly) * 100) 
```

::: panel-tabset
### Generation

```{r}
#| label: generation-generator-comp
#| echo: false
#| message: false

generator_generation_check <- 
  check_generation_diff %>% 
  left_join(generator_monthly %>% 
              select(plant_id, generator_id, prime_mover, gen_data_source_monthly) %>%
              distinct(paste0(plant_id, "_", generator_id, "_", prime_mover), .keep_all = TRUE)) %>%
  select(plant_id, 
         generator_id, 
         prime_mover, 
         gen_data_source_annual,
         gen_data_source_monthly,
         generation_annual,
         generation_monthly,
         generation_diff,
         generation_pct_diff) %>% # ,
         # reporting_frequency,
         # respondent_frequency) %>% 
   filter(generation_diff > 0.01) %>% 
   arrange(-generation_pct_diff)

print(glue::glue("Generation Differences > 0.01: {nrow(generator_generation_check)}"))
```
::: 

## Plant file comparison

The differences between the totals of heat input, emission masses, and generation of the monthly and annual unit files are shown here. The monthly version is aggregated to the annual resolution to compare.

In the tabset below, we list what units have a difference greater than 1 for heat input, emission masses, and generation. 

```{r}
#| label: plant-comparison
#| echo: false
#| message: false

# sum monthly version to annual values
plant_monthly_sum <- 
  plant_monthly_2 %>% 
  group_by(plant_id) %>% 
  summarize(across(.cols = c(contains("heat_input"),
                             contains("generation"), 
                             contains("_mass"), 
                             contains("netgen"), 
                             -contains("source"), 
                             -contains("hg"),
                             -contains("chp")), 
                   .fns = ~ sum(.x, na.rm = TRUE))) %>% 
  ungroup()

# total monthly version 
plant_total_monthly_sum <- 
  plant_monthly_sum %>% 
  summarize(across(.cols = c(contains("heat_input"),
                             contains("generation"), 
                             contains("_mass"), 
                             contains("netgen"), 
                             -contains("source"),
                             -contains("hg"),
                             -contains("chp")), 
                   .fns = ~ sum(.x, na.rm = TRUE), 
                   .names = "{str_replace(.col, '_monthly', '')}")) %>% 
  mutate(agg = "monthly") 

# total annual version to totals
plant_total_annual_sum <- 
  plant_annual %>% 
  summarize(across(.cols = c(contains("heat_input"),
                             contains("generation"), 
                             contains("_mass"), 
                             contains("netgen"), 
                             -contains("source"),
                             -contains("hg"), 
                             -contains("oz"), 
                             -contains("chp"),
                             -contains("sqplt")), 
                   .fns = ~ sum(.x, na.rm = TRUE))) %>% 
  mutate(agg = "annual") 

# calculate difference of total values
plant_total_sum_comp <- 
  rbind(plant_total_monthly_sum, 
        plant_total_annual_sum) %>% 
  relocate(agg) %>% 
  pivot_longer(-c(agg), names_to = "column", values_to = "value") %>% 
  arrange(column) %>% 
  group_by(column) %>% 
  mutate(difference = value - lag(value)) %>% 
  ungroup() %>% 
  mutate(percent_diff = difference / value * 100)

# produce tale of differences of total values
knitr::kable(plant_total_sum_comp,
             digits = 0, 
             format.args = list(big.mark = ","), 
             col.names = gsub("[_]", " ", names(plant_total_sum_comp)), 
             caption = "Plant file totals comparison") %>% 
  scroll_box(width = "100%", height = "500px")

# calculate differences at the unit level
check_plant_diff <- 
  plant_annual_2 %>% 
  full_join(plant_monthly_sum, by = c("plant_id")) %>% 
  mutate(across(.cols = c(contains("heat_input_annual"),
                          "generation_annual",
                          "generation_nonbaseload_annual", 
                          contains("_mass_annual"), 
                          contains("netgen_annual"), 
                          -contains("chp"), 
                          -contains("source"), 
                          -contains("hg"), 
                          -contains("oz")), 
                .fns = ~ abs(.x - get(str_replace(cur_column(), "annual", "monthly"))), 
                .names = "{str_replace(.col, 'annual', 'diff')}"), 
         across(.cols = contains("diff"), 
                .fns = ~ abs(.x / get(str_replace(cur_column(), "diff", "monthly"))) * 100, 
                .names = "{str_replace(.col, 'diff', 'pct_diff')}")) 
```

### Emission rate outliers

```{r}
#| label: calculate-outliers
#| echo: false
#| message: false

# output rates that are negative are typically zeroed out 
# here, we recalculate them and keep the negatives to identify outliers 

plant_rates <- 
  plant_monthly %>% 
  select(month, plant_id, plant_name, generation, heat_input, contains("mass"), contains("rate")) %>%  
  mutate(nox_output_rate = nox_mass / generation * 2000, 
         so2_output_rate = so2_mass / generation * 2000, 
         co2_output_rate = co2_mass/ generation * 2000, 
         ch4_output_rate = ch4_mass / generation, 
         n2o_output_rate = n2o_mass / generation,
         co2e_output_rate = co2e_mass / generation * 2000) 

plant_rates[sapply(plant_rates, is.infinite)] <- NA_real_

plant_stats <- 
  plant_rates %>% 
  mutate(across(.cols = c(contains("rate")), 
                .fns = ~ mean(.x, na.rm = TRUE), 
                .names =  "{.col}_average"), 
         across(.cols = c(contains("rate"), -contains("average")), 
                .fns = ~ sd(.x, na.rm = TRUE), 
                .names =  "{.col}_sd"))

plant_stats[sapply(plant_stats, is.infinite)] <- NA_real_

plant_zscore <- 
  plant_stats %>% 
  mutate(across(.cols = c(contains("rate"), -contains("average"), -contains("sd")), 
                .fns = ~ (.x - mean(.x, na.rm = TRUE)) / sd(.x, na.rm = TRUE), 
                .names =  "{.col}_zscore")) 
```

#### Input rate

::: panel-tabset
##### NOx input rate

```{r}
#| label: plant-nox-input-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(nox_input_rate_zscore > 3 | nox_input_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>%
               filter(nox_input_rate_zscore > 3 | nox_input_rate_zscore < -3) %>% 
               arrange(desc(nox_input_rate_zscore)) %>% 
               select(month, plant_id, plant_name, nox_input_rate_zscore, nox_input_rate))

```

##### SO2 input rate

```{r}
#| label: plant-so2-input-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(so2_input_rate_zscore > 3 | so2_input_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(so2_input_rate_zscore > 3 | so2_input_rate_zscore < -3) %>% 
               arrange(desc(so2_input_rate_zscore)) %>% 
               select(month, plant_id, plant_name, so2_input_rate_zscore, so2_input_rate))
```

##### CO2 input rate

```{r}
#| label: plant-co2-input-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(co2_input_rate_zscore > 3 | co2_input_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(co2_input_rate_zscore > 3 | co2_input_rate_zscore < -3) %>% 
               arrange(desc(co2_input_rate_zscore)) %>% 
               select(month, plant_id, plant_name, co2_input_rate_zscore, co2_input_rate))

```

##### CH4 input rate

```{r}
#| label: plant-ch4-input-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(ch4_input_rate_zscore > 3 | ch4_input_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(ch4_input_rate_zscore > 3 | ch4_input_rate_zscore < -3) %>% 
               arrange(desc(ch4_input_rate_zscore)) %>% 
               select(month, plant_id, plant_name, ch4_input_rate_zscore, ch4_input_rate))

```

##### N2O input rate

```{r}
#| label: plant-n2o-input-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(n2o_input_rate_zscore > 3 | n2o_input_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(n2o_input_rate_zscore > 3 | n2o_input_rate_zscore < -3) %>% 
               arrange(desc(n2o_input_rate_zscore)) %>% 
               select(month, plant_id, plant_name, n2o_input_rate_zscore, n2o_input_rate))

```

##### CO2e input rate

```{r}
#| label: plant-co2e-input-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(co2e_input_rate_zscore > 3 | co2e_input_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(co2e_input_rate_zscore > 3 | co2e_input_rate_zscore < -3) %>% 
               arrange(desc(co2e_input_rate_zscore)) %>% 
               select(month, plant_id, plant_name, co2e_input_rate_zscore, co2e_input_rate))

```
:::

#### Output rates

::: panel-tabset
##### NOx output rate

```{r}
#| label: plant-nox-output-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(nox_output_rate_zscore > 3 | nox_output_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(nox_output_rate_zscore > 3 | nox_output_rate_zscore < -3) %>% 
               arrange(desc(nox_output_rate_zscore)) %>% 
               select(month, plant_id, plant_name, nox_output_rate_zscore, nox_output_rate))

```

##### SO2 output rate

```{r}
#| label: plant-so2-output-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(so2_output_rate_zscore > 3 | so2_output_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(so2_output_rate_zscore > 3 | so2_output_rate_zscore < -3) %>% 
               arrange(desc(so2_output_rate_zscore)) %>% 
               select(month, plant_id, plant_name, so2_output_rate_zscore, so2_output_rate))

```

##### CO2 output rate

```{r}
#| label: plant-co2-output-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(co2_output_rate_zscore > 3 | co2_output_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(co2_output_rate_zscore > 3 | co2_output_rate_zscore < -3) %>% 
               arrange(desc(co2_output_rate_zscore)) %>% 
               select(month, plant_id, plant_name, co2_output_rate_zscore, co2_output_rate))

```

##### CH4 output rate

```{r}
#| label: plant-ch4-output-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(ch4_output_rate_zscore > 3 | ch4_output_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(so2_output_rate_zscore > 3 | so2_output_rate_zscore < -3) %>% 
               arrange(desc(so2_output_rate_zscore)) %>% 
               select(month, plant_id, plant_name, so2_output_rate_zscore, so2_output_rate))

```

##### N2O output rate

```{r}
#| label: plant_n2o_output_outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(n2o_output_rate_zscore > 3 | n2o_output_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(n2o_output_rate_zscore > 3 | n2o_output_rate_zscore < -3) %>% 
               arrange(desc(n2o_output_rate_zscore)) %>% 
               select(month, plant_id, plant_name, n2o_output_rate_zscore, n2o_output_rate))

```

##### CO2e output rate

```{r}
#| label: plant-co2e-output-outliers
#| echo: false
#| message: false

print(glue::glue("z-scores > +/-3: {nrow(plant_zscore %>% 
                 filter(co2e_output_rate_zscore > 3 | co2e_output_rate_zscore < -3))}"))

knitr::kable(plant_zscore %>% 
               filter(co2e_output_rate_zscore > 3 | co2e_output_rate_zscore < -3) %>% 
               arrange(desc(co2e_output_rate_zscore)) %>% 
               select(month, plant_id, plant_name, co2e_output_rate_zscore, co2e_output_rate))

```
:::

### Differences

::: panel-tabset
#### Unadjusted heat input

```{r}
#| label: unadj-heat-input-plant-comp
#| echo: false
#| message: false

options(scipen = 999)

plant_unadj_heat_input_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_heat_input_annual, 
         unadj_heat_input_monthly,
         unadj_heat_input_diff,
         unadj_heat_input_pct_diff) %>% 
   filter(unadj_heat_input_diff > 1) %>% 
   arrange(-unadj_heat_input_pct_diff)

print(glue::glue("Unadjusted Heat Input Differences > 1: {nrow(plant_unadj_heat_input_check)}"))
```

```{r}
#| label: unadj-heat-input-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted Heat Input Annual", 
                           "Unadjusted Heat Input Monthly", 
                           "Unadjusted Heat Input Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted combustion heat input

```{r}
#| label: unadj-combust-heat-input-plant-comp
#| echo: false
#| message: false

plant_unadj_combust_heat_input_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_combust_heat_input_annual, 
         unadj_combust_heat_input_monthly,
         unadj_combust_heat_input_diff,
         unadj_combust_heat_input_pct_diff) %>% 
   filter(unadj_combust_heat_input_diff > 1) %>% 
   arrange(-unadj_combust_heat_input_pct_diff)

print(glue::glue("Unadjusted Combustion Heat Input Differences > 1: {nrow(plant_unadj_combust_heat_input_check)}"))
```

```{r}
#| label: unadj-combust-heat-input-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_combust_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted Combustion Heat Input Annual", 
                           "Unadjusted Combustion Heat Input Monthly", 
                           "Unadjusted Combustion Heat Input Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted combustion heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted NOx mass

```{r}
#| label: unadj-nox-plant-comp
#| echo: false
#| message: false

plant_unadj_nox_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_nox_mass_annual, 
         unadj_nox_mass_monthly,
         unadj_nox_mass_diff,
         unadj_nox_mass_pct_diff) %>% 
   filter(unadj_nox_mass_diff > 1) %>% 
   arrange(-unadj_nox_mass_pct_diff)

print(glue::glue("Unadjusted NOx Differences > 1: {nrow(plant_unadj_nox_check)}"))
```

```{r}
#| label: unadj-nox-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_nox_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted NOx Annual", 
                           "Unadjusted NOx Monthly", 
                           "Unadjusted NOx Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted NOx comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted SO2 mass

```{r}
#| label: unadj-so2-plant-comp
#| echo: false
#| message: false

plant_unadj_so2_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_so2_mass_annual, 
         unadj_so2_mass_monthly,
         unadj_so2_mass_diff,
         unadj_so2_mass_pct_diff) %>% 
   filter(unadj_so2_mass_diff > 1) %>% 
   arrange(-unadj_so2_mass_pct_diff)

print(glue::glue("Unadjusted SO2 Differences > 1: {nrow(plant_unadj_so2_check)}"))
```

```{r}
#| label: unadj-so2-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_so2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted SO2 Annual", 
                           "Unadjusted SO2 Monthly", 
                           "Unadjusted SO2 Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted SO2 comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted CO2 mass

```{r}
#| label: unadj-co2-plant-comp
#| echo: false
#| message: false

plant_unadj_co2_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_co2_mass_annual, 
         unadj_co2_mass_monthly,
         unadj_co2_mass_diff,
         unadj_co2_mass_pct_diff) %>% 
   filter(unadj_co2_mass_diff > 1) %>% 
   arrange(-unadj_co2_mass_pct_diff)

print(glue::glue("Unadjusted CO2 Differences > 1: {nrow(plant_unadj_co2_check)}"))
```

```{r}
#| label: unadj-co2-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_co2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted CO2 Annual", 
                           "Unadjusted CO2 Monthly", 
                           "Unadjusted CO2 Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted CO2 comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted CH4 mass

```{r}
#| label: unadj-ch4-plant-comp
#| echo: false
#| message: false

plant_unadj_ch4_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_ch4_mass_annual, 
         unadj_ch4_mass_monthly,
         unadj_ch4_mass_diff,
         unadj_ch4_mass_pct_diff) %>% 
   filter(unadj_ch4_mass_diff > 1) %>% 
   arrange(-unadj_ch4_mass_pct_diff)

print(glue::glue("Unadjusted CH4 Differences > 1: {nrow(plant_unadj_ch4_check)}"))
```

```{r}
#| label: unadj-ch4-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_ch4_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted CH4 Annual", 
                           "Unadjusted CH4 Monthly", 
                           "Unadjusted CH4 Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted CH4 comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted N2O mass

```{r}
#| label: unadj-n2o-plant-comp
#| echo: false
#| message: false

plant_unadj_n2o_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_n2o_mass_annual, 
         unadj_n2o_mass_monthly,
         unadj_n2o_mass_diff,
         unadj_n2o_mass_pct_diff) %>% 
   filter(unadj_n2o_mass_diff > 1) %>% 
   arrange(-unadj_n2o_mass_pct_diff)

print(glue::glue("Unadjusted N2O Differences > 1: {nrow(plant_unadj_n2o_check)}"))
```

```{r}
#| label: unadj-n2o-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_n2o_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted N2O Annual", 
                           "Unadjusted N2O Monthly", 
                           "Unadjusted N2O Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted N2O comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Unadjusted CO2e mass

```{r}
#| label: unadj-co2e-plant-comp
#| echo: false
#| message: false

plant_unadj_co2e_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         unadj_co2e_mass_annual, 
         unadj_co2e_mass_monthly,
         unadj_co2e_mass_diff,
         unadj_co2e_mass_pct_diff) %>% 
   filter(unadj_co2e_mass_diff > 1) %>% 
   arrange(-unadj_co2e_mass_pct_diff)

print(glue::glue("Unadjusted CO2e Differences > 1: {nrow(plant_unadj_co2e_check)}"))
```

```{r}
#| label: unadj-co2e-plant-table
#| echo: false
#| message: false

knitr::kable(plant_unadj_co2e_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unadjusted CO2e Annual", 
                           "Unadjusted CO2e Monthly", 
                           "Unadjusted CO2e Diff",
                           "Percent Diff"), 
             caption = "Plant file unadjusted CO2e comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Heat input

```{r}
#| label: heat-input-plant-comp
#| echo: false
#| message: false

plant_heat_input_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         heat_input_annual, 
         heat_input_monthly,
         heat_input_diff,
         heat_input_pct_diff) %>% 
   filter(heat_input_diff > 1) %>% 
   arrange(-heat_input_pct_diff)

print(glue::glue("Heat Input Differences > 1: {nrow(plant_heat_input_check)}"))
```

```{r}
#| label: heat-input-plant-table
#| echo: false
#| message: false

knitr::kable(plant_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Heat Input Annual", 
                           "Heat Input Monthly", 
                           "Heat Input Diff",
                           "Percent Diff"), 
             caption = "Plant file heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Combustion heat input

```{r}
#| label: combust-heat-plant-comp
#| echo: false
#| message: false

plant_combust_heat_input_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         combust_heat_input_annual, 
         combust_heat_input_monthly,
         combust_heat_input_diff,
         combust_heat_input_pct_diff) %>% 
   filter(combust_heat_input_diff > 1) %>% 
   arrange(-combust_heat_input_pct_diff)

print(glue::glue("Combustion Heat Input Differences > 1: {nrow(plant_combust_heat_input_check)}"))
```

Notes:

-   Plant 52152 is manually updated in the annual version and needs to be updated at the monthly level.

-   Plant 54638 has 0 generation during months with positive heat input, need to check this. This results in an electric allocation of 0, and a combust heat input of 0. Need to check if cascading issues from generator file.

-   The monthly version of Plant 4005 is correct. This is an EPA plant, so the data may have been updated recently?

```{r}
#| label: combust-heat-plant-table
#| echo: false
#| message: false

knitr::kable(plant_combust_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Combustion Heat Input Annual", 
                           "Combustion Heat Input Monthly", 
                           "Combust Heat Input Diff",
                           "Percent Diff"), 
             caption = "Plant file combustion heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Generation

```{r}
#| label: gen-plant-comp
#| echo: false
#| message: false

plant_gen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         generation_annual, 
         generation_monthly,
         generation_diff,
         generation_pct_diff) %>% 
   filter(generation_diff > 1) %>% 
   arrange(-generation_pct_diff)

print(glue::glue("Generation Differences > 1: {nrow(plant_gen_check)}"))
```

```{r}
#| label: gen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_gen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Generation Annual", 
                           "Generation Monthly", 
                           "Generation Diff",
                           "Percent Diff"), 
             caption = "Plant file generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Generation nonbaseload

```{r}
#| label: gen-nbsld-plant-comp
#| echo: false
#| message: false

plant_gen_nbsld_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         generation_nonbaseload_annual, 
         generation_nonbaseload_monthly,
         generation_nonbaseload_diff,
         generation_nonbaseload_pct_diff) %>% 
   filter(generation_nonbaseload_diff > 1) %>% 
   arrange(-generation_nonbaseload_pct_diff)

print(glue::glue("Generation Nonbaseload Differences > 1: {nrow(plant_gen_nbsld_check)}"))
```

```{r}
#| label: gen-nbsld-plant-table
#| echo: false
#| message: false

knitr::kable(plant_gen_nbsld_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Generation Nonbaseload Annual", 
                           "Generation Nonbaseload Monthly", 
                           "Generation Nonbaseload Diff",
                           "Percent Diff"), 
             caption = "Plant file generation nonbaseload comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### NOx mass

```{r}
#| label: nox-mass-plant-comp
#| echo: false
#| message: false

plant_nox_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         nox_mass_annual, 
         nox_mass_monthly,
         nox_mass_diff,
         nox_mass_pct_diff) %>% 
   filter(nox_mass_diff > 1) %>% 
   arrange(-nox_mass_pct_diff)

print(glue::glue("NOx Mass Differences > 1: {nrow(plant_nox_mass_check)}"))
```

```{r}
#| label: nox-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_nox_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "NOx Mass Annual", 
                           "NOx Mass Monthly", 
                           "NOx Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file NOx mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### SO2 mass

```{r}
#| label: so2-mass-plant-comp
#| echo: false
#| message: false

plant_so2_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         so2_mass_annual, 
         so2_mass_monthly,
         so2_mass_diff,
         so2_mass_pct_diff) %>% 
   filter(so2_mass_diff > 1) %>% 
   arrange(-so2_mass_pct_diff)

print(glue::glue("SO2 Mass Differences > 1: {nrow(plant_so2_mass_check)}"))
```

```{r}
#| label: so2-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_so2_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "SO2 Mass Annual", 
                           "SO2 Mass Monthly", 
                           "SO2 Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file SO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### CO2 mass

```{r}
#| label: co2-mass-plant-comp
#| echo: false
#| message: false

plant_co2_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         co2_mass_annual, 
         co2_mass_monthly,
         co2_mass_diff,
         co2_mass_pct_diff) %>% 
   filter(co2_mass_diff > 1) %>% 
   arrange(-co2_mass_pct_diff)

print(glue::glue("CO2 Mass Differences > 1: {nrow(plant_co2_mass_check)}"))
```

```{r}
#| label: co2-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_co2_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "CO2 Mass Annual", 
                           "CO2 Mass Monthly", 
                           "CO2 Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file CO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### CH4 mass

```{r}
#| label: ch4-mass-plant-comp
#| echo: false
#| message: false

plant_ch4_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         ch4_mass_annual, 
         ch4_mass_monthly,
         ch4_mass_diff,
         ch4_mass_pct_diff) %>% 
   filter(ch4_mass_diff > 1) %>% 
   arrange(-ch4_mass_pct_diff)

print(glue::glue("CH4 Mass Differences > 1: {nrow(plant_ch4_mass_check)}"))
```

```{r}
#| label: ch4-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_ch4_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "CH4 Mass Annual", 
                           "CH4 Mass Monthly", 
                           "CH4 Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file CH4 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### N2O mass

```{r}
#| label: n2o-mass-plant-comp
#| echo: false
#| message: false

plant_n2o_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         n2o_mass_annual, 
         n2o_mass_monthly,
         n2o_mass_diff,
         n2o_mass_pct_diff) %>% 
   filter(n2o_mass_diff > 1) %>% 
   arrange(-n2o_mass_pct_diff)

print(glue::glue("N2O Mass Differences > 1: {nrow(plant_n2o_mass_check)}"))
```

```{r}
#| label: n2o-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_n2o_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "N2O Mass Annual", 
                           "N2O Mass Monthly", 
                           "N2O Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file N2O mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### CO2e mass

```{r}
#| label: co2e-mass-plant-comp
#| echo: false
#| message: false

plant_co2e_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         co2e_mass_annual, 
         co2e_mass_monthly,
         co2e_mass_diff,
         co2e_mass_pct_diff) %>% 
   filter(co2e_mass_diff > 1) %>% 
   arrange(-co2e_mass_pct_diff)

print(glue::glue("CO2e Mass Differences > 1: {nrow(plant_co2e_mass_check)}"))
```

```{r}
#| label: co2e-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_co2e_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "CO2e Mass Annual", 
                           "CO2e Mass Monthly", 
                           "CO2e Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file CO2e mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Coal generation

```{r}
#| label: coal-netgen-plant-comp
#| echo: false
#| message: false

plant_coal_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         coal_netgen_annual, 
         coal_netgen_monthly,
         coal_netgen_diff,
         coal_netgen_pct_diff) %>% 
   filter(coal_netgen_diff > 1) %>% 
   arrange(-coal_netgen_pct_diff)

print(glue::glue("Coal Net Gen Differences > 1: {nrow(plant_coal_netgen_check)}"))
```

```{r}
#| label: coal-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_coal_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Coal Gen Annual", 
                           "Coal Gen Monthly", 
                           "Coal Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file coal generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Oil generation

```{r}
#| label: oil-netgen-plant-comp
#| echo: false
#| message: false

plant_oil_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         oil_netgen_annual, 
         oil_netgen_monthly,
         oil_netgen_diff,
         oil_netgen_pct_diff) %>% 
   filter(oil_netgen_diff > 1) %>% 
   arrange(-oil_netgen_pct_diff)

print(glue::glue("Oil Net Gen Differences > 1: {nrow(plant_oil_netgen_check)}"))
```

```{r}
#| label: oil-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_oil_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Oil Gen Annual", 
                           "Oil Gen Monthly", 
                           "Oil Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file oil generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Gas generation

```{r}
#| label: gas-netgen-plant-comp
#| echo: false
#| message: false

plant_gas_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         gas_netgen_annual, 
         gas_netgen_monthly,
         gas_netgen_diff,
         gas_netgen_pct_diff) %>% 
   filter(gas_netgen_diff > 1) %>% 
   arrange(-gas_netgen_pct_diff)

print(glue::glue("Gas Net Gen Differences > 1: {nrow(plant_gas_netgen_check)}"))
```

```{r}
#| label: gas-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_gas_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Gas Gen Annual", 
                           "Gas Gen Monthly", 
                           "Gas Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file gas generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Nuclear generation

```{r}
#| label: nuclear-netgen-plant-comp
#| echo: false
#| message: false

plant_nuclear_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         nuclear_netgen_annual, 
         nuclear_netgen_monthly,
         nuclear_netgen_diff,
         nuclear_netgen_pct_diff) %>% 
   filter(nuclear_netgen_diff > 1) %>% 
   arrange(-nuclear_netgen_pct_diff)

print(glue::glue("Nuclear Net Gen Differences > 1: {nrow(plant_nuclear_netgen_check)}"))
```

```{r}
#| label: nuclear-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_nuclear_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Nuclear Gen Annual", 
                           "Nuclear Gen Monthly", 
                           "Nuclear Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file nuclear generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Hydro generation

```{r}
#| label: hydro-netgen-plant-comp
#| echo: false
#| message: false

plant_hydro_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         hydro_netgen_annual, 
         hydro_netgen_monthly,
         hydro_netgen_diff,
         hydro_netgen_pct_diff) %>% 
   filter(hydro_netgen_diff > 1) %>% 
   arrange(-hydro_netgen_pct_diff)

print(glue::glue("Hydro Net Gen Differences > 1: {nrow(plant_hydro_netgen_check)}"))
```

```{r}
#| label: hydro-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_hydro_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Hydro Gen Annual", 
                           "Hydro Gen Monthly", 
                           "Hydro Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file hydro generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Biomass generation

```{r}
#| label: biomass-netgen-plant-comp
#| echo: false
#| message: false

plant_biomass_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         biomass_netgen_annual, 
         biomass_netgen_monthly,
         biomass_netgen_diff,
         biomass_netgen_pct_diff) %>% 
   filter(biomass_netgen_diff > 1) %>% 
   arrange(-biomass_netgen_pct_diff)

print(glue::glue("Biomass Net Gen Differences > 1: {nrow(plant_biomass_netgen_check)}"))
```

```{r}
#| label: biomass-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_biomass_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Biomass Gen Annual", 
                           "Biomass Gen Monthly", 
                           "Biomass Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file biomass generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Wind generation

```{r}
#| label: wind-netgen-plant-comp
#| echo: false
#| message: false

plant_wind_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         wind_netgen_annual, 
         wind_netgen_monthly,
         wind_netgen_diff,
         wind_netgen_pct_diff) %>% 
   filter(wind_netgen_diff > 1) %>% 
   arrange(-wind_netgen_pct_diff)

print(glue::glue("Wind Net Gen Differences > 1: {nrow(plant_wind_netgen_check)}"))
```

```{r}
#| label: wind-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_wind_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Wind Gen Annual", 
                           "Wind Gen Monthly", 
                           "Wind Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file wind generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Solar generation

```{r}
#| label: solar-netgen-plant-comp
#| echo: false
#| message: false

plant_solar_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         solar_netgen_annual, 
         solar_netgen_monthly,
         solar_netgen_diff,
         solar_netgen_pct_diff) %>% 
   filter(solar_netgen_diff > 1) %>% 
   arrange(-solar_netgen_pct_diff)

print(glue::glue("Solar Net Gen Differences > 1: {nrow(plant_solar_netgen_check)}"))
```

```{r}
#| label: solar-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_solar_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Solar Gen Annual", 
                           "Solar Gen Monthly", 
                           "Solar Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file solar generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Geothermal generation

```{r}
#| label: geothermal-netgen-plant-comp
#| echo: false
#| message: false

plant_geothermal_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         geothermal_netgen_annual, 
         geothermal_netgen_monthly,
         geothermal_netgen_diff,
         geothermal_netgen_pct_diff) %>% 
   filter(geothermal_netgen_diff > 1) %>% 
   arrange(-geothermal_netgen_pct_diff)

print(glue::glue("Geothermal Net Gen Differences > 1: {nrow(plant_geothermal_netgen_check)}"))
```

```{r}
#| label: geothermal-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_geothermal_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Geothermal Gen Annual", 
                           "Geothermal Gen Monthly", 
                           "Geothermal Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file geothermal generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Other fossil fuels

```{r}
#| label: other-ff-netgen-plant-comp
#| echo: false
#| message: false

plant_other_ff_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         other_ff_netgen_annual, 
         other_ff_netgen_monthly,
         other_ff_netgen_diff,
         other_ff_netgen_pct_diff) %>% 
   filter(other_ff_netgen_diff > 1) %>% 
   arrange(-other_ff_netgen_pct_diff)

print(glue::glue("Other Fossil Net Gen Differences > 1: {nrow(plant_other_ff_netgen_check)}"))
```

```{r}
#| label: other-ff-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_other_ff_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Other Fossil Gen Annual", 
                           "Other Fossil Gen Monthly", 
                           "Other Fossil Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file other fossil generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

#### Other generation

```{r}
#| label: other-netgen-plant-comp
#| echo: false
#| message: false

plant_other_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         other_netgen_annual, 
         other_netgen_monthly,
         other_netgen_diff,
         other_netgen_pct_diff) %>% 
   filter(other_netgen_diff > 1) %>% 
   arrange(-other_netgen_pct_diff)

print(glue::glue("Other Net Gen Differences > 1: {nrow(plant_other_netgen_check)}"))
```

```{r}
#| label: other-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_other_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Other Gen Annual", 
                           "Other Gen Monthly", 
                           "Other Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file other generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

:::
