---
title: "Monthly Production Model QA"
format: html
editor: visual
table-of-contents: true
---

```{r}
#| label: load-libraries
#| echo: false
#| message: false

library(dplyr)
library(ggplot2)
library(kableExtra)
library(readr)
library(tidyr)
library(patchwork)

```

```{r}
#| label: read-format-data
#| echo: false
#| message: false

# load in unit data, format, and merge
unit_monthly <- 
  read_rds("data/outputs/2023/unit_file_monthly.RDS")

colnames(unit_monthly) <- paste0(colnames(unit_monthly), "_monthly")
unit_monthly <- unit_monthly %>% 
  rename("plant_id" = "plant_id_monthly",
         "unit_id" = "unit_id_monthly", 
         "prime_mover" = "prime_mover_monthly",
         "year" = "year_monthly",
         "month" = "month_monthly") %>% 
  mutate(month = as.character(month))

unit_annual <- 
  read_rds("data/outputs/2023/unit_file_annual.RDS")

colnames(unit_annual) <- paste0(colnames(unit_annual), "_annual")
unit_annual <- unit_annual %>% 
  rename("plant_id" = "plant_id_annual",
         "unit_id" = "unit_id_annual", 
         "prime_mover" = "prime_mover_annual",  
         "year" = "year_annual") %>% 
  mutate(month = "annual")

# load in plant data, format, and merge
plant_monthly <- 
  read_rds("data/outputs/2023/plant_file_monthly.RDS") %>% 
  mutate(month = as.character(month))

plant_annual <- 
  read_rds("data/outputs/2023/plant_file.RDS") %>% 
  mutate(month = "annual")

plant_merged <-
  plant_monthly %>% 
  full_join(plant_annual)

plant_merged$month <- factor(plant_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in state data, format, and merge
state_monthly <- 
  read_rds("data/outputs/2023/state_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

state_annual <- 
  read_rds("data/outputs/2023/state_aggregation.RDS") %>% 
  mutate(month = "annual")

state_merged <-
  state_monthly %>% 
  full_join(state_annual)

state_merged$month <- factor(state_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in BA data, format, and merge
ba_monthly <- 
  read_rds("data/outputs/2023/ba_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

ba_annual <- 
  read_rds("data/outputs/2023/ba_aggregation.RDS") %>% 
  mutate(month = "annual")

ba_merged <-
  ba_monthly %>% 
  full_join(ba_annual)

ba_merged$month <- factor(ba_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in subregion data, format, and merge
subregion_monthly <- 
  read_rds("data/outputs/2023/subregion_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

subregion_annual <- 
  read_rds("data/outputs/2023/subregion_aggregation.RDS") %>% 
  mutate(month = "annual")

subregion_merged <-
  subregion_monthly %>% 
  full_join(subregion_annual)

subregion_merged$month <- factor(subregion_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in NERC data, format, and merge
nerc_monthly <- 
  read_rds("data/outputs/2023/nerc_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

nerc_annual <- 
  read_rds("data/outputs/2023/nerc_aggregation.RDS") %>% 
  mutate(month = "annual")

nerc_merged <-
  nerc_monthly %>% 
  full_join(nerc_annual)

nerc_merged$month <- factor(nerc_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in US data, format, and merge
us_monthly <- 
  read_rds("data/outputs/2023/us_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

us_annual <- 
  read_rds("data/outputs/2023/us_aggregation.RDS") %>% 
  mutate(month = "annual")

us_merged <-
  us_monthly %>% 
  full_join(us_annual)

us_merged$month <- factor(us_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

```

## Unit file comparison

The differences between the totals of heat input and emission masses of the monthly and annual unit files are shown here. In the tabset below, we list what units have a difference greater than 0.01 for heat input and emission masses. We also note which units are ozone reporters, since the methodology for filling non-ozone months is different between annual (non-ozone distributed) and monthly (non-ozone filled via EIA and summed to annual) versions for heat input and annual NOx mass.

```{r}
#| label: unit-comparison
#| echo: false
#| message: false

# read in EPA data to identify OS reporters
epa <- 
  read_rds("data/clean_data/epa/2023/epa_clean_annual.RDS") %>% 
  select(plant_id, unit_id, reporting_frequency) %>% 
  distinct()

# sum monthly version to annual values
unit_monthly_sum <- 
  unit_monthly %>% 
  group_by(plant_id, unit_id, prime_mover) %>% 
  summarize(heat_input_monthly = sum(heat_input_monthly, na.rm = TRUE), 
            nox_mass_monthly = sum(nox_mass_monthly, na.rm = TRUE), 
            so2_mass_monthly = sum(so2_mass_monthly, na.rm = TRUE), 
            co2_mass_monthly = sum(co2_mass_monthly, na.rm = TRUE)) %>% 
  ungroup()

# total monthly version 
unit_total_monthly_sum <- 
  unit_monthly_sum %>% 
  summarize(heat_input = sum(heat_input_monthly, na.rm = TRUE), 
            nox_mass = sum(nox_mass_monthly, na.rm = TRUE),
            so2_mass = sum(so2_mass_monthly, na.rm = TRUE), 
            co2_mass = sum(co2_mass_monthly, na.rm = TRUE)) %>% 
  mutate(agg = "monthly") 

# total annual version to totals
unit_total_annual_sum <- 
  unit_annual %>% 
  summarize(heat_input = sum(heat_input_annual, na.rm = TRUE), 
            nox_mass = sum(nox_mass_annual, na.rm = TRUE), 
            so2_mass = sum(so2_mass_annual, na.rm = TRUE), 
            co2_mass = sum(co2_mass_annual, na.rm = TRUE)) %>% 
  mutate(agg = "annual") 

# calculate difference of total values
unit_total_sum_comp <- 
  rbind(unit_total_monthly_sum, 
        unit_total_annual_sum) %>% 
  relocate(agg) %>% 
  pivot_longer(-c(agg), names_to = "column", values_to = "value") %>% 
  arrange(column) %>% 
  group_by(column) %>% 
  mutate(difference = value - lag(value)) 

# produce tale of differences of total values
knitr::kable(unit_total_sum_comp,
             digits = 0, 
             format.args = list(big.mark = ","), 
             col.names = gsub("[_]", " ", names(unit_total_sum_comp)), 
             caption = "Unit file totals comparison") 

# calculate differences at the unit level
check_unit_diff <- 
  unit_annual %>% 
  full_join(unit_monthly_sum, by = c("plant_id", "unit_id", "prime_mover")) %>% 
  mutate(heat_input_diff = abs(heat_input_annual - heat_input_monthly), 
         heat_input_pct_diff = abs(heat_input_diff / heat_input_monthly) * 100,
         nox_diff = abs(nox_mass_annual - nox_mass_monthly),
         nox_pct_diff = abs(nox_diff / nox_mass_monthly) * 100,
         so2_diff = abs(so2_mass_annual - so2_mass_monthly), 
         so2_pct_diff = abs(so2_diff / so2_mass_monthly) * 100,
         co2_diff = abs(co2_mass_annual - co2_mass_monthly),
         co2_pct_diff = abs(co2_diff / co2_mass_monthly) * 100) %>% 
  left_join(epa, by = c("plant_id", "unit_id")) %>% 
  select(plant_id, unit_id, prime_mover, 
         heat_input_diff, 
         heat_input_pct_diff,
         nox_diff,
         nox_pct_diff,
         so2_diff,
         so2_pct_diff, 
         co2_diff,
         co2_pct_diff, 
         reporting_frequency)
```

::: panel-tabset
## Heat input

Notes:

-   Plant 52152 Unit ID 6RB heat input is manually corrected in the annual version. We will need to implement this change at the monthly level.

-   All other differences are attributable to the difference in ozone season methodology.

```{r}
#| label: heat-input-unit-comp
#| echo: false
#| message: false

unit_heat_input_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         heat_input_diff,
         heat_input_pct_diff,
         reporting_frequency) %>% 
   filter(heat_input_diff > 0.01) %>% 
   arrange(-heat_input_diff)

print(glue::glue("Heat Input Differences > 0.01: {nrow(unit_heat_input_check)}"))

knitr::kable(unit_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "Heat Input Diff",
                           "Percent Diff",
                           "Reporting Frequency"), 
             caption = "Unit file heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")



```

## NOx mass

Notes:

-   Plant 52152 Unit ID 6RB NOx mass is manually corrected in the annual version. We will need to implement this change at the monthly level.

-   A few NOx mass differences are attributable to differences in ozone season methodology.

```{r}
#| label: nox-unit-comp
#| echo: false
#| message: false

unit_nox_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         nox_diff,
         nox_pct_diff,
         reporting_frequency) %>% 
   filter(nox_diff > 0.01) %>% 
   arrange(-nox_diff)

print(glue::glue("NOx mass differences > 0.01: {nrow(unit_nox_check)}"))

knitr::kable(unit_nox_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "Annual NOx Diff",
                           "Percent Diff",
                           "Reporting Frequency"), 
             caption = "Unit file NOx mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```

## SO2 mass

Notes:

-   Plant 52152 Unit ID 6RB SO2 mass is manually corrected in the annual version. We will need to implement this change at the monthly level.

-   Some differences are due to differences across sulfur content since annual is an average of all monthly sulfur contents, but we use monthly level sulfur contents for the monthly version. 

```{r}
#| label: so2-unit-comp
#| echo: false
#| message: false

unit_so2_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         so2_diff,
         so2_pct_diff) %>% 
  filter(so2_diff > 0.01) %>% 
  arrange(-so2_diff)

print(glue::glue("SO2 mass differences > 0.01: {nrow(unit_so2_check)}"))

knitr::kable(unit_so2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "Annual SO2 Diff",
                           "Percent Diff"), 
             caption = "Unit file SO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```

## CO2 mass

Notes:

-   Plant 52152 Unit ID 6RB CO2 mass is manually corrected in the annual version. We will need to implement this change at the monthly level.

```{r}
#| label: co2-unit-comp
#| echo: false
#| message: false

unit_co2_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         co2_diff,
         co2_pct_diff) %>% 
  filter(co2_diff > 0.01) %>% 
  arrange(-co2_diff)

print(glue::glue("CO2 mass differences > 0.01: {nrow(unit_co2_check)}"))

knitr::kable(unit_co2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "Annual CO2 Diff",
                           "Percent Diff"), 
             caption = "Unit file CO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```
:::

## Subregion file comparison

::: panel-tabset
### Summary

This tabset shows the output and input rates for each subregion. An average line is shown across the months. 

### AKGD

```{r}
#| label: subregion-akgd
#| echo: false
#| message: false
#| fig-height: 4

subregion_akgd <- 
  subregion_merged %>% 
  filter(subregion == "AKGD")

# output rates
plot_nox_output_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akgd$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akgd$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akgd$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akgd$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akgd$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_akgd %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akgd$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akgd$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)

```

### AKMS

```{r}
#| label: subregion-akms
#| echo: false
#| message: false
#| fig-height: 4

subregion_akms <- 
  subregion_merged %>% 
  filter(subregion == "AKMS")

# output rates
plot_nox_output_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akms$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akms$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akms$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akms$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_akms$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_akms %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_akms$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_akms$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### AZNM

```{r}
#| label: subregion-aznm
#| echo: false
#| message: false
#| fig-height: 4

subregion_aznm <- 
  subregion_merged %>% 
  filter(subregion == "AZNM")

# output rates
plot_nox_output_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_aznm$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_aznm$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_aznm$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_aznm$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_aznm$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_aznm %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_aznm$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_aznm$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### CAMX

```{r}
#| label: subregion-camx
#| echo: false
#| message: false
#| fig-height: 4

subregion_camx <- 
  subregion_merged %>% 
  filter(subregion == "CAMX")

# output rates
plot_nox_output_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_camx$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_camx$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_camx$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_camx$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_camx$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_camx %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_camx$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_camx$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### FRCC

```{r}
#| label: subregion-frcc
#| echo: false
#| message: false
#| fig-height: 4

subregion_frcc <- 
  subregion_merged %>% 
  filter(subregion == "FRCC")

# output rates
plot_nox_output_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_frcc$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_frcc$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_frcc$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_frcc$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_frcc$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_frcc %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_frcc$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_frcc$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### HIMS

```{r}
#| label: subregion-hims
#| echo: false
#| message: false
#| fig-height: 4

subregion_hims <- 
  subregion_merged %>% 
  filter(subregion == "HIMS")

# output rates
plot_nox_output_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hims$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hims$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hims$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hims$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hims$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_hims %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hims$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hims$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### HIOA

```{r}
#| label: subregion-hioa
#| echo: false
#| message: false
#| fig-height: 4

subregion_hioa <- 
  subregion_merged %>% 
  filter(subregion == "HIOA")

# output rates
plot_nox_output_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hioa$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hioa$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hioa$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_hioa$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hioa$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_hioa$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hioa$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hioa$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hioa$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hioa$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y = mean(subregion_hioa$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_hioa %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_hioa$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_hioa$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### MROE

```{r}
#| label: subregion-mroe
#| echo: false
#| message: false
#| fig-height: 4

subregion_mroe <- 
  subregion_merged %>% 
  filter(subregion == "MROE")

# output rates
plot_nox_output_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_mroe$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_mroe$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_mroe$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_mroe$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_mroe$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_mroe %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_mroe$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_mroe$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### MROW

```{r}

```

### NEWE

```{r}

```

### NWPP

```{r}

```

### NYCW

```{r}

```

### NYLI

```{r}

```

### NYUP

```{r}

```

### PRMS

```{r}

```

### RFCE

```{r}

```

### RFCM

```{r}

```

### RFCW

```{r}

```

### RMPA

```{r}

```

### SPNO

```{r}

```

### SPSO

```{r}

```

### SRMV

```{r}

```

### SRSO

```{r}

```

### SRTV

```{r}

```

### SRVC

```{r}

```
:::

## State file comparison

::: panel-tabset
### AK

```{r}

```

### AL

```{r}

```

### AR

```{r}

```

### AZ

```{r}

```

### CA

```{r}

```

### CO

```{r}

```

### CT

```{r}

```

### DC

```{r}

```

### DE

```{r}

```

### FL

```{r}

```

### GA

```{r}

```

### HI

```{r}

```

### IA

```{r}

```

### ID

```{r}

```

### IL

```{r}

```

### IN

```{r}

```

### KS

```{r}

```

### KY

```{r}

```

### LA

```{r}

```

### MA

```{r}

```

### MD

```{r}

```

### ME

```{r}

```

### MI

```{r}

```

### MN

```{r}

```

### MO

```{r}

```

### MS

```{r}

```

### MT

```{r}

```

### NC

```{r}

```

### ND

```{r}

```

### NE

```{r}

```

### NH

```{r}

```

### NJ

```{r}

```

### NM

```{r}

```

### NV

```{r}

```

### NY

```{r}

```

### OH

```{r}

```

### OK

```{r}

```

### OR

```{r}

```

### PA

```{r}

```

### PR

```{r}

```

### RI

```{r}

```

### SC

```{r}

```

### SD

```{r}

```

### TN

```{r}

```

### TX

```{r}

```

### UT

```{r}

```

### VA

```{r}

```

### VT

```{r}

```

### WA

```{r}

```

### WI

```{r}

```

### WV

```{r}

```

### WY

```{r}

```
:::
