---
title: "Monthly Production Model QA"
format: html
editor: visual
table-of-contents: true
---

```{r}
#| label: load-libraries
#| echo: false
#| message: false

library(dplyr)
library(ggplot2)
library(kableExtra)
library(readr)
library(tidyr)
library(patchwork)
library(stringr)

```

```{r}
#| label: load-functions
#| echo: false
#| message: false

source("scripts/qa/monthly_qa/function_plot_monthly_comparison.R")
base::load("data/static_tables/name_matches.RData")
```


```{r}
#| label: read-format-data
#| echo: false
#| message: false

# load in unit data, format, and merge
unit_monthly <- 
  read_rds("data/outputs/2023/unit_file_monthly.RDS")

colnames(unit_monthly) <- paste0(colnames(unit_monthly), "_monthly")
unit_monthly <- unit_monthly %>% 
  rename("plant_id" = "plant_id_monthly",
         "unit_id" = "unit_id_monthly", 
         "prime_mover" = "prime_mover_monthly",
         "year" = "year_monthly",
         "month" = "month_monthly") %>% 
  mutate(month = as.character(month))

unit_annual <- 
  read_rds("data/outputs/2023/unit_file_annual.RDS")

colnames(unit_annual) <- paste0(colnames(unit_annual), "_annual")
unit_annual <- unit_annual %>% 
  rename("plant_id" = "plant_id_annual",
         "unit_id" = "unit_id_annual", 
         "prime_mover" = "prime_mover_annual",  
         "year" = "year_annual") %>% 
  mutate(month = "annual")

# load in plant data, format, and merge
plant_monthly <- 
  read_rds("data/outputs/2023/plant_file_monthly.RDS") %>% 
  mutate(month = as.character(month))

plant_monthly_2 <- plant_monthly
colnames(plant_monthly_2) <- paste0(colnames(plant_monthly_2), "_monthly")
plant_monthly_2 <- 
  plant_monthly_2 %>% 
  rename("plant_id" = "plant_id_monthly",
         "year" = "year_monthly",
         "month" = "month_monthly") %>% 
  mutate(month = as.character(month))

plant_annual <- 
  read_rds("data/outputs/2023/plant_file.RDS") 

# rename to new version of column names
new_vars <- 
  plant_nonmetric_annual
colnames(plant_annual) <- new_vars
  
plant_annual_2 <- plant_annual
colnames(plant_annual_2) <- paste0(colnames(plant_annual_2), "_annual")
plant_annual_2 <- 
  plant_annual_2 %>% 
  rename("plant_id" = "plant_id_annual",
         "year" = "year_annual") 

plant_merged <-
  plant_monthly %>% 
  full_join(plant_annual %>% mutate(month = "annual"))

plant_merged$month <- factor(plant_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in state data, format, and merge
state_monthly <- 
  read_rds("data/outputs/2023/state_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

state_annual <- 
  read_rds("data/outputs/2023/state_aggregation.RDS") %>% 
  mutate(month = "annual")

state_merged <-
  state_monthly %>% 
  full_join(state_annual)

state_merged$month <- factor(state_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in BA data, format, and merge
ba_monthly <- 
  read_rds("data/outputs/2023/ba_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

ba_annual <- 
  read_rds("data/outputs/2023/ba_aggregation.RDS") %>% 
  mutate(month = "annual")

ba_merged <-
  ba_monthly %>% 
  full_join(ba_annual)

ba_merged$month <- factor(ba_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in subregion data, format, and merge
subregion_monthly <- 
  read_rds("data/outputs/2023/subregion_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

subregion_annual <- 
  read_rds("data/outputs/2023/subregion_aggregation.RDS") %>% 
  mutate(month = "annual")

subregion_merged <-
  subregion_monthly %>% 
  full_join(subregion_annual)

subregion_merged$month <- factor(subregion_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in NERC data, format, and merge
nerc_monthly <- 
  read_rds("data/outputs/2023/nerc_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

nerc_annual <- 
  read_rds("data/outputs/2023/nerc_aggregation.RDS") %>% 
  mutate(month = "annual")

nerc_merged <-
  nerc_monthly %>% 
  full_join(nerc_annual)

nerc_merged$month <- factor(nerc_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

# load in US data, format, and merge
us_monthly <- 
  read_rds("data/outputs/2023/us_aggregation_monthly.RDS") %>% 
  mutate(month = as.character(month))

us_annual <- 
  read_rds("data/outputs/2023/us_aggregation.RDS") %>% 
  mutate(month = "annual")

us_merged <-
  us_monthly %>% 
  full_join(us_annual)

us_merged$month <- factor(us_merged$month, 
                             levels = c("1", "2", "3", "4", "5", "6", 
                                        "7", "8", "9", "10", "11", "12", "annual"))

```

## Unit file comparison

The differences between the totals of heat input and emission masses of the monthly and annual unit files are shown here. The monthly version is aggregated to the annual resolution to compare. 

In the tabset below, we list what units have a difference greater than 0.01 for heat input and emission masses. We also note which units are ozone reporters, since the methodology for filling non-ozone months is different between annual (non-ozone distributed) and monthly (non-ozone filled via EIA and summed to annual) versions for heat input and annual NOx mass.


```{r}
#| label: unit-comparison
#| echo: false
#| message: false

# read in EPA data to identify OS reporters
epa <- 
  read_rds("data/clean_data/epa/2023/epa_clean_annual.RDS") %>% 
  select(plant_id, unit_id, reporting_frequency) %>% 
  distinct()

# sum monthly version to annual values
unit_monthly_sum <- 
  unit_monthly %>% 
  group_by(plant_id, unit_id, prime_mover) %>% 
  summarize(heat_input_monthly = sum(heat_input_monthly, na.rm = TRUE), 
            nox_mass_monthly = sum(nox_mass_monthly, na.rm = TRUE), 
            so2_mass_monthly = sum(so2_mass_monthly, na.rm = TRUE), 
            co2_mass_monthly = sum(co2_mass_monthly, na.rm = TRUE)) %>% 
  ungroup()

# total monthly version 
unit_total_monthly_sum <- 
  unit_monthly_sum %>% 
  summarize(heat_input = sum(heat_input_monthly, na.rm = TRUE), 
            nox_mass = sum(nox_mass_monthly, na.rm = TRUE),
            so2_mass = sum(so2_mass_monthly, na.rm = TRUE), 
            co2_mass = sum(co2_mass_monthly, na.rm = TRUE)) %>% 
  mutate(agg = "monthly") 

# total annual version to totals
unit_total_annual_sum <- 
  unit_annual %>% 
  summarize(heat_input = sum(heat_input_annual, na.rm = TRUE), 
            nox_mass = sum(nox_mass_annual, na.rm = TRUE), 
            so2_mass = sum(so2_mass_annual, na.rm = TRUE), 
            co2_mass = sum(co2_mass_annual, na.rm = TRUE)) %>% 
  mutate(agg = "annual") 

# calculate difference of total values
unit_total_sum_comp <- 
  rbind(unit_total_monthly_sum, 
        unit_total_annual_sum) %>% 
  relocate(agg) %>% 
  pivot_longer(-c(agg), names_to = "column", values_to = "value") %>% 
  arrange(column) %>% 
  group_by(column) %>% 
  mutate(difference = value - lag(value)) 

# produce tale of differences of total values
knitr::kable(unit_total_sum_comp,
             digits = 0, 
             format.args = list(big.mark = ","), 
             col.names = gsub("[_]", " ", names(unit_total_sum_comp)), 
             caption = "Unit file totals comparison") 

# calculate differences at the unit level
check_unit_diff <- 
  unit_annual %>% 
  full_join(unit_monthly_sum, by = c("plant_id", "unit_id", "prime_mover")) %>% 
  mutate(heat_input_diff = abs(heat_input_annual - heat_input_monthly), 
         heat_input_pct_diff = abs(heat_input_diff / heat_input_monthly) * 100,
         nox_diff = abs(nox_mass_annual - nox_mass_monthly),
         nox_pct_diff = abs(nox_diff / nox_mass_monthly) * 100,
         so2_diff = abs(so2_mass_annual - so2_mass_monthly), 
         so2_pct_diff = abs(so2_diff / so2_mass_monthly) * 100,
         co2_diff = abs(co2_mass_annual - co2_mass_monthly),
         co2_pct_diff = abs(co2_diff / co2_mass_monthly) * 100) %>% 
  left_join(epa, by = c("plant_id", "unit_id")) 
```

::: panel-tabset

### Heat input

```{r}
#| label: heat-input-unit-comp
#| echo: false
#| message: false

unit_heat_input_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         heat_input_annual,
         heat_input_monthly,
         heat_input_diff,
         heat_input_pct_diff,
         reporting_frequency) %>% 
   filter(heat_input_diff > 0.01) %>% 
   arrange(-heat_input_diff)

print(glue::glue("Heat Input Differences > 0.01: {nrow(unit_heat_input_check)}"))
```


Notes:

-   Plant 52152 Unit ID 6RB heat input is manually corrected in the annual version. We will need to implement this change at the monthly level.

-   All other differences are attributable to the difference in ozone season methodology.

```{r}
#| label: heat-input-unit-table
#| echo: false
#| message: false

knitr::kable(unit_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "Heat Input Annual",
                           "Heat Input Monthly",
                           "Heat Input Diff",
                           "Percent Diff",
                           "Reporting Frequency"), 
             caption = "Unit file heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### NOx mass

```{r}
#| label: nox-unit-comp
#| echo: false
#| message: false

unit_nox_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         nox_mass_annual,
         nox_mass_monthly,
         nox_diff,
         nox_pct_diff,
         reporting_frequency) %>% 
   filter(nox_diff > 0.01) %>% 
   arrange(-nox_diff)

print(glue::glue("NOx mass differences > 0.01: {nrow(unit_nox_check)}"))
```

Notes:

-   Plant 52152 Unit ID 6RB NOx mass is manually corrected in the annual version. We will need to implement this change at the monthly level.

-   A few NOx mass differences are attributable to differences in ozone season methodology.

-   Plant 62289 Units use fuel consumption physical units for monthly, which underestimates emissions compared to using heat input. 

```{r}
#| label: nox-unit-table
#| echo: false
#| message: false

knitr::kable(unit_nox_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "NOx Mass Annual", 
                           "NOx Mass Monthly", 
                           "Annual NOx Diff",
                           "Percent Diff",
                           "Reporting Frequency"), 
             caption = "Unit file NOx mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```

### SO2 mass

```{r}
#| label: so2-unit-comp
#| echo: false
#| message: false

unit_so2_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         so2_mass_annual,
         so2_mass_monthly,
         so2_diff,
         so2_pct_diff) %>% 
  filter(so2_diff > 0.01) %>% 
  arrange(-so2_diff)

print(glue::glue("SO2 mass differences > 0.01: {nrow(unit_so2_check)}"))
```


Notes:

-   Plant 52152 Unit ID 6RB SO2 mass is manually corrected in the annual version. We will need to implement this change at the monthly level.

-   Some differences are due to differences across sulfur content since annual is an average of all monthly sulfur contents, but we use monthly level sulfur contents for the monthly version.

```{r}
#| label: so2-unit-table
#| echo: false
#| message: false

knitr::kable(unit_so2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "SO2 Mass Annual", 
                           "SO2 Mass Monthly", 
                           "Annual SO2 Diff",
                           "Percent Diff"), 
             caption = "Unit file SO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```

### CO2 mass

```{r}
#| label: co2-unit-comp
#| echo: false
#| message: false

unit_co2_check <- 
  check_unit_diff %>% 
  select(plant_id, 
         unit_id, 
         prime_mover, 
         co2_mass_annual, 
         co2_mass_monthly, 
         co2_diff,
         co2_pct_diff) %>% 
  filter(co2_diff > 0.01) %>% 
  arrange(-co2_diff) 

print(glue::glue("CO2 mass differences > 0.01: {nrow(unit_co2_check)}"))
```


Notes:

-   Plant 52152 Unit ID 6RB CO2 mass is manually corrected in the annual version. We will need to implement this change at the monthly level.

```{r}
#| label: co2-unit-table
#| echo: false
#| message: false

knitr::kable(unit_co2_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Unit ID", 
                           "Prime Mover",
                           "CO2 Mass Annual", 
                           "CO2 Mass Monthly", 
                           "Annual CO2 Diff",
                           "Percent Diff"), 
             caption = "Unit file CO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")

```
:::

## Plant file comparison

```{r}
#| label: plant-comparison
#| echo: false
#| message: false

# sum monthly version to annual values
plant_monthly_sum <- 
  plant_monthly_2 %>% 
  group_by(plant_id) %>% 
  summarize(across(.cols = c(contains("heat_input"),
                             contains("generation"), 
                             contains("_mass"), 
                             contains("netgen"), 
                             -contains("source"), 
                             -contains("hg"),
                             -contains("chp")), 
                   .fns = ~ sum(.x, na.rm = TRUE))) %>% 
  ungroup()

# total monthly version 
plant_total_monthly_sum <- 
  plant_monthly_sum %>% 
  summarize(across(.cols = c(contains("heat_input"),
                             contains("generation"), 
                             contains("_mass"), 
                             contains("netgen"), 
                             -contains("source"),
                             -contains("hg"),
                             -contains("chp")), 
                   .fns = ~ sum(.x, na.rm = TRUE), 
                   .names = "{str_replace(.col, '_monthly', '')}")) %>% 
  mutate(agg = "monthly") 

# total annual version to totals
plant_total_annual_sum <- 
  plant_annual %>% 
  summarize(across(.cols = c(contains("heat_input"),
                             contains("generation"), 
                             contains("_mass"), 
                             contains("netgen"), 
                             -contains("source"),
                             -contains("hg"), 
                             -contains("oz"), 
                             -contains("chp")), 
                   .fns = ~ sum(.x, na.rm = TRUE))) %>% 
  mutate(agg = "annual") 

# calculate difference of total values
plant_total_sum_comp <- 
  rbind(plant_total_monthly_sum, 
        plant_total_annual_sum) %>% 
  relocate(agg) %>% 
  pivot_longer(-c(agg), names_to = "column", values_to = "value") %>% 
  arrange(column) %>% 
  group_by(column) %>% 
  mutate(difference = value - lag(value)) 

# produce tale of differences of total values
knitr::kable(plant_total_sum_comp,
             digits = 0, 
             format.args = list(big.mark = ","), 
             col.names = gsub("[_]", " ", names(plant_total_sum_comp)), 
             caption = "Plant file totals comparison") %>% 
  scroll_box(width = "100%", height = "500px")

# calculate differences at the unit level
check_plant_diff <- 
  plant_annual_2 %>% 
  full_join(plant_monthly_sum, by = c("plant_id")) %>% 
  mutate(across(.cols = c(contains("heat_input_annual"),
                          "generation_annual",
                          "generation_nonbaseload_annual", 
                          contains("_mass_annual"), 
                          contains("netgen_annual"), 
                          -contains("chp"), 
                          -contains("source"), 
                          -contains("hg"), 
                          -contains("oz")), 
                .fns = ~ abs(.x - get(str_replace(cur_column(), "annual", "monthly"))), 
                .names = "{str_replace(.col, 'annual', 'diff')}"), 
         across(.cols = contains("diff"), 
                .fns = ~ abs(.x / get(str_replace(cur_column(), "diff", "monthly"))) * 100, 
                .names = "{str_replace(.col, 'diff', 'pct_diff')}")) 
```

::: panel-tabset

### Heat input 

```{r}
#| label: heat-input-plant-comp
#| echo: false
#| message: false

plant_heat_input_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         heat_input_annual, 
         heat_input_monthly,
         heat_input_diff,
         heat_input_pct_diff) %>% 
   filter(heat_input_diff > 1) %>% 
   arrange(-heat_input_pct_diff)

print(glue::glue("Heat Input Differences > 1: {nrow(plant_heat_input_check)}"))
```

```{r}
#| label: heat-input-plant-table
#| echo: false
#| message: false

knitr::kable(plant_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Heat Input Annual", 
                           "Heat Input Monthly", 
                           "Heat Input Diff",
                           "Percent Diff"), 
             caption = "Plant file heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### Combustion heat input

```{r}
#| label: combust-heat-plant-comp
#| echo: false
#| message: false

plant_combust_heat_input_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         combust_heat_input_annual, 
         combust_heat_input_monthly,
         combust_heat_input_diff,
         combust_heat_input_pct_diff) %>% 
   filter(combust_heat_input_diff > 1) %>% 
   arrange(-combust_heat_input_pct_diff)

print(glue::glue("Combustion Heat Input Differences > 1: {nrow(plant_combust_heat_input_check)}"))
```

Notes: 

-   Plant 52152 is manually updated in the annual version and needs to be updated at the monthly level. 

-   Plant 54638 has 0 generation during months with positive heat input, need to check this. This results in an electric allocation of 0, and a combust heat input of 0. Need to check if cascading issues from generator file.

-   The monthly version of Plant 4005 is correct. This is an EPA plant, so the data may have been updated recently? 

```{r}
#| label: combust-heat-plant-table
#| echo: false
#| message: false

knitr::kable(plant_combust_heat_input_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Combustion Heat Input Annual", 
                           "Combustion Heat Input Monthly", 
                           "Combust Heat Input Diff",
                           "Percent Diff"), 
             caption = "Plant file combustion heat input comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### Generation

```{r}
#| label: gen-plant-comp
#| echo: false
#| message: false

plant_gen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         generation_annual, 
         generation_monthly,
         generation_diff,
         generation_pct_diff) %>% 
   filter(generation_diff > 1) %>% 
   arrange(-generation_pct_diff)

print(glue::glue("Generation Differences > 1: {nrow(plant_gen_check)}"))
```

```{r}
#| label: gen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_gen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Generation Annual", 
                           "Generation Monthly", 
                           "Generation Diff",
                           "Percent Diff"), 
             caption = "Plant file generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### Generation nonbaseload

```{r}
#| label: gen-nbsld-plant-comp
#| echo: false
#| message: false

plant_gen_nbsld_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         generation_nonbaseload_annual, 
         generation_nonbaseload_monthly,
         generation_nonbaseload_diff,
         generation_nonbaseload_pct_diff) %>% 
   filter(generation_nonbaseload_diff > 1) %>% 
   arrange(-generation_nonbaseload_pct_diff)

print(glue::glue("Generation Nonbaseload Differences > 1: {nrow(plant_gen_nbsld_check)}"))
```

```{r}
#| label: gen-nbsld-plant-table
#| echo: false
#| message: false

knitr::kable(plant_gen_nbsld_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Generation Nonbaseload Annual", 
                           "Generation Nonbaseload Monthly", 
                           "Generation Nonbaseload Diff",
                           "Percent Diff"), 
             caption = "Plant file generation nonbaseload comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### NOx mass

```{r}
#| label: nox-mass-plant-comp
#| echo: false
#| message: false

plant_nox_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         nox_mass_annual, 
         nox_mass_monthly,
         nox_mass_diff,
         nox_mass_pct_diff) %>% 
   filter(nox_mass_diff > 1) %>% 
   arrange(-nox_mass_pct_diff)

print(glue::glue("NOx Mass Differences > 1: {nrow(plant_nox_mass_check)}"))
```

```{r}
#| label: nox-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_nox_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "NOx Mass Annual", 
                           "NOx Mass Monthly", 
                           "NOx Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file NOx mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### SO2 mass

```{r}
#| label: so2-mass-plant-comp
#| echo: false
#| message: false

plant_so2_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         so2_mass_annual, 
         so2_mass_monthly,
         so2_mass_diff,
         so2_mass_pct_diff) %>% 
   filter(so2_mass_diff > 1) %>% 
   arrange(-so2_mass_pct_diff)

print(glue::glue("SO2 Mass Differences > 1: {nrow(plant_so2_mass_check)}"))
```

```{r}
#| label: so2-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_so2_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "SO2 Mass Annual", 
                           "SO2 Mass Monthly", 
                           "SO2 Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file SO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### CO2 mass

```{r}
#| label: co2-mass-plant-comp
#| echo: false
#| message: false

plant_co2_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         co2_mass_annual, 
         co2_mass_monthly,
         co2_mass_diff,
         co2_mass_pct_diff) %>% 
   filter(co2_mass_diff > 1) %>% 
   arrange(-co2_mass_pct_diff)

print(glue::glue("CO2 Mass Differences > 1: {nrow(plant_co2_mass_check)}"))
```

```{r}
#| label: co2-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_co2_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "CO2 Mass Annual", 
                           "CO2 Mass Monthly", 
                           "CO2 Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file CO2 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### CH4 mass

```{r}
#| label: ch4-mass-plant-comp
#| echo: false
#| message: false

plant_ch4_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         ch4_mass_annual, 
         ch4_mass_monthly,
         ch4_mass_diff,
         ch4_mass_pct_diff) %>% 
   filter(ch4_mass_diff > 1) %>% 
   arrange(-ch4_mass_pct_diff)

print(glue::glue("CH4 Mass Differences > 1: {nrow(plant_ch4_mass_check)}"))
```

```{r}
#| label: ch4-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_ch4_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "CH4 Mass Annual", 
                           "CH4 Mass Monthly", 
                           "CH4 Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file CH4 mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### N2O mass

```{r}
#| label: n2o-mass-plant-comp
#| echo: false
#| message: false

plant_n2o_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         n2o_mass_annual, 
         n2o_mass_monthly,
         n2o_mass_diff,
         n2o_mass_pct_diff) %>% 
   filter(n2o_mass_diff > 1) %>% 
   arrange(-n2o_mass_pct_diff)

print(glue::glue("N2O Mass Differences > 1: {nrow(plant_n2o_mass_check)}"))
```

```{r}
#| label: n2o-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_n2o_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "N2O Mass Annual", 
                           "N2O Mass Monthly", 
                           "N2O Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file N2O mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### CO2e mass

```{r}
#| label: co2e-mass-plant-comp
#| echo: false
#| message: false

plant_co2e_mass_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         co2e_mass_annual, 
         co2e_mass_monthly,
         co2e_mass_diff,
         co2e_mass_pct_diff) %>% 
   filter(co2e_mass_diff > 1) %>% 
   arrange(-co2e_mass_pct_diff)

print(glue::glue("CO2e Mass Differences > 1: {nrow(plant_co2e_mass_check)}"))
```

```{r}
#| label: co2e-mass-plant-table
#| echo: false
#| message: false

knitr::kable(plant_co2e_mass_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "CO2e Mass Annual", 
                           "CO2e Mass Monthly", 
                           "CO2e Mass Diff",
                           "Percent Diff"), 
             caption = "Plant file CO2e mass comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### Coal generation

```{r}
#| label: coal-netgen-plant-comp
#| echo: false
#| message: false

plant_coal_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         coal_netgen_annual, 
         coal_netgen_monthly,
         coal_netgen_diff,
         coal_netgen_pct_diff) %>% 
   filter(coal_netgen_diff > 1) %>% 
   arrange(-coal_netgen_pct_diff)

print(glue::glue("Coal Net Gen Differences > 1: {nrow(plant_coal_netgen_check)}"))
```

```{r}
#| label: coal-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_coal_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Coal Gen Annual", 
                           "Coal Gen Monthly", 
                           "Coal Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file coal generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### Oil generation

```{r}
#| label: oil-netgen-plant-comp
#| echo: false
#| message: false

plant_oil_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         oil_netgen_annual, 
         oil_netgen_monthly,
         oil_netgen_diff,
         oil_netgen_pct_diff) %>% 
   filter(oil_netgen_diff > 1) %>% 
   arrange(-oil_netgen_pct_diff)

print(glue::glue("Oil Net Gen Differences > 1: {nrow(plant_oil_netgen_check)}"))
```

```{r}
#| label: oil-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_oil_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Oil Gen Annual", 
                           "Oil Gen Monthly", 
                           "Oil Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file oil generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

### Gas generation

```{r}
#| label: gas-netgen-plant-comp
#| echo: false
#| message: false

plant_gas_netgen_check <- 
  check_plant_diff %>% 
  select(plant_id, 
         gas_netgen_annual, 
         gas_netgen_monthly,
         gas_netgen_diff,
         gas_netgen_pct_diff) %>% 
   filter(gas_netgen_diff > 1) %>% 
   arrange(-gas_netgen_pct_diff)

print(glue::glue("Gas Net Gen Differences > 1: {nrow(plant_gas_netgen_check)}"))
```

```{r}
#| label: gas-netgen-plant-table
#| echo: false
#| message: false

knitr::kable(plant_gas_netgen_check,
             digits = 2, 
             format.args = list(big.mark = ","), 
             col.names = c("Plant ID", 
                           "Gas Gen Annual", 
                           "Gas Gen Monthly", 
                           "Gas Gen Diff",
                           "Percent Diff"), 
             caption = "Plant file gas generation comparison") %>% 
  scroll_box(width = "100%", height = "500px")
```

:::

## Subregion file comparison

```{r}
#| label: subregion-avg
#| echo: false
#| message: false 

subregion_avg <- 
  subregion_merged %>% 
  filter(month != "annual") %>% 
  group_by(subregion) %>% 
  summarize(nox_out_mean = mean(subregion_nox_output_rate, na.rm = TRUE), 
            so2_out_mean = mean(subregion_so2_output_rate, na.rm = TRUE), 
            co2_out_mean = mean(subregion_co2_output_rate, na.rm = TRUE), 
            ch4_out_mean = mean(subregion_ch4_output_rate, na.rm = TRUE), 
            n2o_out_mean = mean(subregion_n2o_output_rate, na.rm = TRUE), 
            co2e_out_mean = mean(subregion_co2e_output_rate, na.rm = TRUE), 
            nox_in_mean = mean(subregion_nox_input_rate, na.rm = TRUE), 
            so2_in_mean = mean(subregion_so2_input_rate, na.rm = TRUE), 
            co2_in_mean = mean(subregion_co2_input_rate, na.rm = TRUE), 
            ch4_in_mean = mean(subregion_ch4_input_rate, na.rm = TRUE), 
            n2o_in_mean = mean(subregion_n2o_input_rate, na.rm = TRUE), 
            co2e_in_mean = mean(subregion_co2e_input_rate, na.rm = TRUE))
```


::: panel-tabset
### Summary

This tabset shows the output and input rates for each subregion. The black dotted line displays the monthly average. 

### AKGD

```{r}
#| label: subregion-akgd
#| echo: false
#| message: false
#| fig-height: 4

subregion_akgd <- 
  subregion_merged %>% 
  filter(subregion == "AKGD") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_akgd$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_akgd$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_akgd$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_akgd$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_akgd$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_akgd$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_akgd$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_akgd$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_akgd$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_akgd$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_akgd$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_akgd$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_akgd$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_akgd$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_akgd$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_akgd$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_akgd$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_akgd$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_akgd$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_akgd$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_akgd$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_akgd$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_akgd, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_akgd$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akgd,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_akgd$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### AKMS

```{r}
#| label: subregion-akms
#| echo: false
#| message: false
#| fig-height: 4

subregion_akms <- 
  subregion_merged %>% 
  filter(subregion == "AKMS") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_akms$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_akms$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_akms$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_akms$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_akms$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_akms$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_akms$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_akms$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_akms$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_akms$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_akms$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_akms$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_akms$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_akms$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_akms$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_akms$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_akms$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_akms$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_akms$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_akms$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_akms$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_akms$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_akms, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_akms$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_akms,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_akms$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### AZNM

```{r}
#| label: subregion-aznm
#| echo: false
#| message: false
#| fig-height: 4

subregion_aznm <- 
  subregion_merged %>% 
  filter(subregion == "AZNM") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_aznm$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_aznm$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_aznm$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_aznm$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_aznm$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_aznm$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_aznm$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_aznm$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_aznm$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_aznm$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_aznm$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_aznm$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_aznm$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_aznm$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_aznm$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_aznm$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_aznm$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_aznm$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_aznm$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_aznm$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_aznm$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_aznm$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_aznm, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_aznm$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_aznm,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_aznm$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### CAMX

```{r}
#| label: subregion-camx
#| echo: false
#| message: false
#| fig-height: 4

subregion_camx <- 
  subregion_merged %>% 
  filter(subregion == "CAMX") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_camx$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_camx$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_camx$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_camx$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_camx$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_camx$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_camx$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_camx$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_camx$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_camx$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_camx$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_camx$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_camx$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_camx$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_camx$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_camx$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_camx$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_camx$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_camx$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_camx$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_camx$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_camx$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_camx, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_camx$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_camx,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_camx$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### FRCC

```{r}
#| label: subregion-frcc
#| echo: false
#| message: false
#| fig-height: 4

subregion_frcc <- 
  subregion_merged %>% 
  filter(subregion == "FRCC") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_frcc$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_frcc$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_frcc$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_frcc$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_frcc$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_frcc$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_frcc$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_frcc$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_frcc$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_frcc$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_frcc$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_frcc$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_frcc$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_frcc$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_frcc$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_frcc$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_frcc$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_frcc$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_frcc$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_frcc$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_frcc$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_frcc$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_frcc, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_frcc$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_frcc,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_frcc$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### HIMS

```{r}
#| label: subregion-hims
#| echo: false
#| message: false
#| fig-height: 4

subregion_hims <- 
  subregion_merged %>% 
  filter(subregion == "HIMS") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_hims$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_hims$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_hims$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_hims$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_hims$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_hims$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_hims$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_hims$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_hims$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_hims$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_hims$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_hims$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_hims$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_hims$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_hims$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_hims$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_hims$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_hims$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_hims$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_hims$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_hims$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_hims$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_hims, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_hims$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hims,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_hims$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### HIOA

```{r}
#| label: subregion-hioa
#| echo: false
#| message: false
#| fig-height: 4

subregion_hioa <- 
  subregion_merged %>% 
  filter(subregion == "HIOA") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_hioa$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_hioa$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_hioa$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_hioa$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_hioa$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_hioa$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_hioa$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_hioa$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_hioa$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_hioa$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_hioa$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_hioa$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_hioa$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_hioa$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_hioa$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_hioa$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_hioa$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_hioa$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_hioa$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_hioa$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_hioa$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_hioa$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_hioa, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_hioa$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_hioa,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_hioa$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### MROE

```{r}
#| label: subregion-mroe
#| echo: false
#| message: false
#| fig-height: 4

subregion_mroe <- 
  subregion_merged %>% 
  filter(subregion == "MROE") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_mroe$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_mroe$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_mroe$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_mroe$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_mroe$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_mroe$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_mroe$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_mroe$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_mroe$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_mroe$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_mroe$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_mroe$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_mroe$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_mroe$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_mroe$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_mroe$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_mroe$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_mroe$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_mroe$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_mroe$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_mroe$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_mroe$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_mroe, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_mroe$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mroe,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_mroe$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### MROW

```{r}
#| label: subregion-mrow
#| echo: false
#| message: false
#| fig-height: 4

subregion_mrow <- 
  subregion_merged %>% 
  filter(subregion == "MROW") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_mrow$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_mrow$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_mrow$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_mrow$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_mrow$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_mrow$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_mrow$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_mrow$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_mrow$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_mrow$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_mrow$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_mrow$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_mrow$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_mrow$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_mrow$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_mrow$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_mrow$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_mrow$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_mrow$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_mrow$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_mrow$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_mrow$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_mrow, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_mrow$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_mrow,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_mrow$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### NEWE

```{r}
#| label: subregion-newe
#| echo: false
#| message: false
#| fig-height: 4

subregion_newe <- 
  subregion_merged %>% 
  filter(subregion == "NEWE") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_newe$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_newe$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_newe$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_newe$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_newe$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_newe$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_newe$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_newe$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_newe$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_newe$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_newe$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_newe$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_newe$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_newe$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_newe$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_newe$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_newe$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_newe$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_newe$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_newe$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_newe$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_newe$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_newe, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_newe$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_newe,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_newe$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### NWPP

```{r}
#| label: subregion-nwpp
#| echo: false
#| message: false
#| fig-height: 4

subregion_nwpp <- 
  subregion_merged %>% 
  filter(subregion == "NWPP") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_nwpp$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_nwpp$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_nwpp$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_nwpp$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_nwpp$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_nwpp$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_nwpp$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_nwpp$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_nwpp$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_nwpp$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_nwpp$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_nwpp$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_nwpp$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_nwpp$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_nwpp$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_nwpp$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_nwpp$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_nwpp$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_nwpp$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_nwpp$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_nwpp$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_nwpp$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_nwpp, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_nwpp$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nwpp,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_nwpp$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### NYCW

```{r}
#| label: subregion-nycw
#| echo: false
#| message: false
#| fig-height: 4

subregion_nycw <- 
  subregion_merged %>% 
  filter(subregion == "NYCW") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_nycw$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_nycw$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_nycw$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_nycw$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_nycw$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_nycw$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_nycw$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_nycw$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_nycw$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_nycw$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_nycw$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_nycw$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_nycw$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_nycw$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_nycw$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_nycw$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_nycw$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_nycw$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_nycw$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_nycw$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_nycw$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_nycw$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_nycw, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_nycw$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nycw,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_nycw$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### NYLI

```{r}
#| label: subregion-nyli
#| echo: false
#| message: false
#| fig-height: 4

subregion_nyli <- 
  subregion_merged %>% 
  filter(subregion == "NYLI")

# output rates
plot_nox_output_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_nyli$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_nyli$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_nyli$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_nyli$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_nyli$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_nyli %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_nyli$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_nyli$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### NYUP

```{r}
#| label: subregion-nyup
#| echo: false
#| message: false
#| fig-height: 4

subregion_nyup <- 
  subregion_merged %>% 
  filter(subregion == "NYUP") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_nyup$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_nyup$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_nyup$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_nyup$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_nyup$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_nyup$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_nyup$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_nyup$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_nyup$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_nyup$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_nyup$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_nyup$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_nyup$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_nyup$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_nyup$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_nyup$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_nyup$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_nyup$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_nyup$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_nyup$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_nyup$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_nyup$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_nyup, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_nyup$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_nyup,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_nyup$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### PRMS

```{r}
#| label: subregion-prms
#| echo: false
#| message: false
#| fig-height: 4

subregion_prms <- 
  subregion_merged %>% 
  filter(subregion == "PRMS") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_prms$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_prms$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_prms$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_prms$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_prms$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_prms$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_prms$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_prms$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_prms$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_prms$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_prms$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_prms$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_prms$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_prms$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_prms$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_prms$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_prms$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_prms$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_prms$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_prms$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_prms$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_prms$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_prms, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_prms$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_prms,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_prms$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### RFCE

```{r}
#| label: subregion-rfce
#| echo: false
#| message: false
#| fig-height: 4

subregion_rfce <- 
  subregion_merged %>% 
  filter(subregion == "RFCE") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_rfce$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_rfce$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_rfce$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_rfce$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_rfce$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_rfce$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_rfce$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_rfce$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_rfce$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_rfce$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_rfce$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_rfce$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_rfce$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_rfce$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_rfce$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_rfce$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_rfce$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_rfce$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_rfce$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_rfce$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_rfce$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_rfce$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_rfce, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_rfce$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfce,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_rfce$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### RFCM

```{r}
#| label: subregion-rfcm
#| echo: false
#| message: false
#| fig-height: 4

subregion_rfcm <- 
  subregion_merged %>% 
  filter(subregion == "RFCM") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_rfcm$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_rfcm$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_rfcm$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_rfcm$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_rfcm$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_rfcm$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_rfcm$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_rfcm$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_rfcm$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_rfcm$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_rfcm$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_rfcm$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_rfcm$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_rfcm$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_rfcm$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_rfcm$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_rfcm$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_rfcm$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_rfcm$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_rfcm$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_rfcm$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_rfcm$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_rfcm, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_rfcm$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rfcm,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_rfcm$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### RFCW

```{r}
#| label: subregion-rfcw
#| echo: false
#| message: false
#| fig-height: 4

subregion_rfcw <- 
  subregion_merged %>% 
  filter(subregion == "RFCW")

# output rates
plot_nox_output_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_nox_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Output Rate") + 
  xlab("Time period") + 
  ylab("NOx output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_nox_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_rfcw$subregion_nox_output_rate)/12)

plot_so2_output_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_so2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Output Rate") +
  xlab("Time period") + 
  ylab("SO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_so2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_rfcw$subregion_so2_output_rate)/12)

plot_co2_output_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_co2_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Output Rate") +
  xlab("Time period") + 
  ylab("CO2 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_co2_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_rfcw$subregion_co2_output_rate)/12)

plot_ch4_output_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_ch4_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Output Rate") +
  xlab("Time period") + 
  ylab("CH4 output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_ch4_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_output_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_ch4_output_rate)/12)

plot_n2o_output_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_n2o_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Output Rate") +
  xlab("Time period") + 
  ylab("N2O output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_n2o_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_rfcw$subregion_n2o_output_rate)/12)

plot_co2e_output_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_co2e_output_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Output Rate") +
  xlab("Time period") + 
  ylab("CO2e output rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_co2e_output_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_output_rate)), label = "AVG", 
                nudge_y = mean(subregion_rfcw$subregion_co2e_output_rate)/12)

# input rates
plot_nox_input_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_nox_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("NOx Input Rate") + 
  xlab("Time period") + 
  ylab("NOx input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_nox_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_nox_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_nox_input_rate)/12)

plot_so2_input_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_so2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("SO2 Input Rate") +
  xlab("Time period") + 
  ylab("SO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_so2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_so2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_so2_input_rate)/12)

plot_co2_input_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_co2_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2 Input Rate") +
  xlab("Time period") + 
  ylab("CO2 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_co2_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_co2_input_rate)/12)

plot_ch4_input_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_ch4_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CH4 Input Rate") +
  xlab("Time period") + 
  ylab("CH4 input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_ch4_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_ch4_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_ch4_input_rate)/12)

plot_n2o_input_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_n2o_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("N2O Input Rate") +
  xlab("Time period") + 
  ylab("N2O input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_n2o_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_n2o_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_n2o_input_rate)/12)

plot_co2e_input_rate <- 
  subregion_rfcw %>% 
  ggplot(aes(x = month, y = subregion_co2e_input_rate, fill = month)) +
  geom_bar(stat = "identity") + 
  ggtitle("CO2e Input Rate") +
  xlab("Time period") + 
  ylab("CO2e input rate") + 
  scale_fill_manual(values = c("deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "deepskyblue3", "deepskyblue3", "deepskyblue3", "deepskyblue3", 
                               "firebrick3")) + 
  theme(legend.position = "none") + 
  geom_hline(yintercept = mean(subregion_rfcw$subregion_co2e_input_rate, na.rm = TRUE), 
             linetype = "dashed", show.legend = TRUE) + 
  geom_text(aes(x = 1, y = mean(subregion_co2e_input_rate)), label = "AVG", 
                nudge_y =mean(subregion_rfcw$subregion_co2e_input_rate)/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### RMPA

```{r}
#| label: subregion-rmpa
#| echo: false
#| message: false
#| fig-height: 4

subregion_rmpa <- 
  subregion_merged %>% 
  filter(subregion == "RMPA") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_rmpa$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_rmpa$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_rmpa$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_rmpa$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_rmpa$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_rmpa$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_rmpa$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_rmpa$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_rmpa$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_rmpa$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_rmpa$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_rmpa$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_rmpa$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_rmpa$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_rmpa$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_rmpa$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_rmpa$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_rmpa$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_rmpa$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_rmpa$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_rmpa$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_rmpa$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_rmpa, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_rmpa$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_rmpa,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_rmpa$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### SPNO

```{r}
#| label: subregion-spno
#| echo: false
#| message: false
#| fig-height: 4

subregion_spno <- 
  subregion_merged %>% 
  filter(subregion == "SPNO") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_spno$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_spno$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_spno$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_spno$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_spno$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_spno$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_spno$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_spno$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_spno$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_spno$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_spno$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_spno$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_spno$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_spno$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_spno$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_spno$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_spno$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_spno$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_spno$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_spno$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_spno$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_spno$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_spno, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_spno$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spno,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_spno$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### SPSO

```{r}
#| label: subregion-spso
#| echo: false
#| message: false
#| fig-height: 4

subregion_spso <- 
  subregion_merged %>% 
  filter(subregion == "SPSO") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_spso$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_spso$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_spso$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_spso$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_spso$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_spso$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_spso$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_spso$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_spso$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_spso$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_spso$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_spso$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_spso$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_spso$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_spso$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_spso$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_spso$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_spso$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_spso$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_spso$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_spso$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_spso$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_spso, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_spso$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_spso,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_spso$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### SRMV

```{r}
#| label: subregion-srmv
#| echo: false
#| message: false
#| fig-height: 4

subregion_srmv <- 
  subregion_merged %>% 
  filter(subregion == "SRMV") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_srmv$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_srmv$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_srmv$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_srmv$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_srmv$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_srmv$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_srmv$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_srmv$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_srmv$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_srmv$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_srmv$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_srmv$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_srmv$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_srmv$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_srmv$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_srmv$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_srmv$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_srmv$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_srmv$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_srmv$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_srmv$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_srmv$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_srmv, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_srmv$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srmv,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_srmv$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### SRSO

```{r}
#| label: subregion-srso
#| echo: false
#| message: false
#| fig-height: 4

subregion_srso <- 
  subregion_merged %>% 
  filter(subregion == "SRSO") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_srso$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_srso$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_srso$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_srso$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_srso$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_srso$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_srso$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_srso$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_srso$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_srso$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_srso$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_srso$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_srso$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_srso$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_srso$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_srso$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_srso$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_srso$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_srso$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_srso$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_srso$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_srso$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_srso, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_srso$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srso,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_srso$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### SRTV

```{r}
#| label: subregion-srtv
#| echo: false
#| message: false
#| fig-height: 4

subregion_srtv <- 
  subregion_merged %>% 
  filter(subregion == "SRTV") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_srtv$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_srtv$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_srtv$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_srtv$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_srtv$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_srtv$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_srtv$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_srtv$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_srtv$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_srtv$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_srtv$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_srtv$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_srtv$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_srtv$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_srtv$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_srtv$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_srtv$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_srtv$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_srtv$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_srtv$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_srtv$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_srtv$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_srtv, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_srtv$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srtv,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_srtv$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```

### SRVC

```{r}
#| label: subregion-srvc
#| echo: false
#| message: false
#| fig-height: 4

subregion_srvc <- 
  subregion_merged %>% 
  filter(subregion == "SRVC") %>% 
  left_join(subregion_avg, by = c("subregion"))

# output rates
plot_nox_output_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_nox_output_rate,  
                          "NOx output rate") + 
  geom_hline(yintercept = subregion_srvc$nox_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = nox_out_mean), label = "AVG", 
            nudge_y = subregion_srvc$nox_out_mean/12)

plot_so2_output_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_so2_output_rate,  
                          "SO2 output rate") + 
  geom_hline(yintercept = subregion_srvc$so2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = so2_out_mean), label = "AVG", 
            nudge_y = subregion_srvc$so2_out_mean/12)

plot_co2_output_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_co2_output_rate,  
                          "CO2 output rate") + 
  geom_hline(yintercept = subregion_srvc$co2_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = co2_out_mean), label = "AVG", 
            nudge_y = subregion_srvc$co2_out_mean/12)

plot_ch4_output_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_ch4_output_rate,  
                          "CH4 output rate") + 
  geom_hline(yintercept = subregion_srvc$ch4_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = ch4_out_mean), label = "AVG", 
            nudge_y = subregion_srvc$ch4_out_mean/12)

plot_n2o_output_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_n2o_output_rate,  
                          "N2O output rate") + 
  geom_hline(yintercept = subregion_srvc$n2o_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = n2o_out_mean), label = "AVG", 
            nudge_y = subregion_srvc$n2o_out_mean/12)

plot_co2e_output_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_co2e_output_rate,  
                          "CO2e output rate") + 
  geom_hline(yintercept = subregion_srvc$co2e_out_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = co2e_out_mean), label = "AVG", 
            nudge_y = subregion_srvc$co2e_out_mean/12)

# input rates
plot_nox_input_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_nox_input_rate,  
                          "NOx input rate") + 
  geom_hline(yintercept = subregion_srvc$nox_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = nox_in_mean), label = "AVG", 
            nudge_y = subregion_srvc$nox_in_mean/12)

plot_so2_input_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_so2_input_rate,  
                          "SO2 input rate") + 
  geom_hline(yintercept = subregion_srvc$so2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = so2_in_mean), label = "AVG", 
            nudge_y = subregion_srvc$so2_in_mean/12)

plot_co2_input_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_co2_input_rate,  
                          "CO2 input rate") + 
  geom_hline(yintercept = subregion_srvc$co2_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = co2_in_mean), label = "AVG", 
            nudge_y = subregion_srvc$co2_in_mean/12)

plot_ch4_input_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_ch4_input_rate,  
                          "CH4 input rate") + 
  geom_hline(yintercept = subregion_srvc$ch4_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = ch4_in_mean), label = "AVG", 
            nudge_y = subregion_srvc$ch4_in_mean/12)

plot_n2o_input_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_n2o_input_rate,  
                          "N2O input rate") + 
  geom_hline(yintercept = subregion_srvc$n2o_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = n2o_in_mean), label = "AVG", 
            nudge_y = subregion_srvc$n2o_in_mean/12)

plot_co2e_input_rate <- 
  plot_monthly_comparison(subregion_srvc, 
                          subregion_co2e_input_rate,  
                          "CO2e input rate") + 
  geom_hline(yintercept = subregion_srvc$co2e_in_mean, 
             linetype = "dashed") + 
  geom_text(data = subregion_srvc,
            aes(x = 1, y = co2e_in_mean), label = "AVG", 
            nudge_y = subregion_srvc$co2e_in_mean/12)

plotly::ggplotly(plot_nox_output_rate) 
plotly::ggplotly(plot_so2_output_rate)  
plotly::ggplotly(plot_co2_output_rate)
plotly::ggplotly(plot_ch4_output_rate)
plotly::ggplotly(plot_n2o_output_rate)
plotly::ggplotly(plot_co2e_output_rate)

plotly::ggplotly(plot_nox_input_rate) 
plotly::ggplotly(plot_so2_input_rate)  
plotly::ggplotly(plot_co2_input_rate)
plotly::ggplotly(plot_ch4_input_rate)
plotly::ggplotly(plot_n2o_input_rate)
plotly::ggplotly(plot_co2e_input_rate)
```
:::

## State file comparison

::: panel-tabset
### AK

```{r}

```

### AL

```{r}

```

### AR

```{r}

```

### AZ

```{r}

```

### CA

```{r}

```

### CO

```{r}

```

### CT

```{r}

```

### DC

```{r}

```

### DE

```{r}

```

### FL

```{r}

```

### GA

```{r}

```

### HI

```{r}

```

### IA

```{r}

```

### ID

```{r}

```

### IL

```{r}

```

### IN

```{r}

```

### KS

```{r}

```

### KY

```{r}

```

### LA

```{r}

```

### MA

```{r}

```

### MD

```{r}

```

### ME

```{r}

```

### MI

```{r}

```

### MN

```{r}

```

### MO

```{r}

```

### MS

```{r}

```

### MT

```{r}

```

### NC

```{r}

```

### ND

```{r}

```

### NE

```{r}

```

### NH

```{r}

```

### NJ

```{r}

```

### NM

```{r}

```

### NV

```{r}

```

### NY

```{r}

```

### OH

```{r}

```

### OK

```{r}

```

### OR

```{r}

```

### PA

```{r}

```

### PR

```{r}

```

### RI

```{r}

```

### SC

```{r}

```

### SD

```{r}

```

### TN

```{r}

```

### TX

```{r}

```

### UT

```{r}

```

### VA

```{r}

```

### VT

```{r}

```

### WA

```{r}

```

### WI

```{r}

```

### WV

```{r}

```

### WY

```{r}

```
:::
