---
title: "eGRID PM2.5, NH3, and VOC Emission Estimates"
author: 
  - "Emma Russell, Abt Global"
freeze: true
format: 
  html:
    toc: true
    toc-expand: true
    toc-depth: 2
    toc-location: left
    html-table-processing: none
    code-fold: true
execute: 
  message: false
  warning: false
  results: hold
  eval: false
params:
  eGRID_year: "2021"

editor: visual
project: 
  execute_dir: project
---

# Overview

This project includes all necessary scripts and documentation to create the Emissions & Generation Resource Integrated Database (eGRID) particulate matter (PM~2.5~), ammonia (NH~3~), and volatile organic compound (VOC) emission estimates.

# Background

eGRID is a comprehensive source of data from [EPA's Clean Air and Power Division (CAPD)](https://epa.gov/power-sector) on the environmental characteristics of almost all electric power generated in the United States. Currently, eGRID includes emissions data on carbon dioxide (CO~2~), nitrogen oxides (NO~X~), sulfur dioxide (SO~2~), methane (CH~4~), and nitrous oxide (N~2~O), but does not include PM~2.5~, NH~3~, and VOC emissions. The data used for emission calculations in eGRID is not available for PM~2.5~, NH~3~, and VOCs and is instead collected from the National Emissions Inventory (NEI).

Here we use NEI data to determine PM~2.5~, NH~3~, and VOC emissions and emission rates as well as estimate emissions for units that may not report to the NEI.

The final emissions datasets include four levels of data aggregation:

-   **Unit**: A set of equipment that either produces electricity and is connected to the U.S electricity grid or a set of equipment that is connected to a generator which produces electricity and is connected to the U.S. electricity grid.

-   **Plant**: A facility with one or more units and/or generators that provide power to the electric grid.

-   **State**: U.S. states, Puerto Rico (PR), and the District of Columbia (DC).

-   **eGRID subregion**: EPA defined subregions designed to limit the impacts of the import and export of electricity.

-   **National U.S.**: Contains all 50 states, Puerto Rico (PR), and the District of Columbia (DC).

Further information on the eGRID PM~2.5~, NH~3~, and VOC methodology can be found in the [Particulate Matter Emissions for eGRID2021](https://www.epa.gov/system/files/documents/2024-06/egrid2021-draft-pm-memo.pdf).

The dataset that this code produces is publicly available [here](https://www.epa.gov/egrid/egrid-pm25).

## Using the .qmd file

This is a Quarto (.qmd) file that documents and runs the code necessary to create the eGRID PM~2.5~, NH~3~, and VOC datasets. This document can be used in two ways: First, when used within an IDE, such as RStudio, it serves as an enhanced master script, allowing users to easily perform each step necessary to create the eGRID PM~2.5~, NH~3~, and VOC data from within a single file. Second, when viewing as a rendered file, it provides thorough documentation of the steps involved in creating the emissiond data. When rendered, this file provides additional information and tools for navigating the project. The table of contents provides both a convenient look at the project structure and method for navigating the document. There are also hidden code chunks throughout, marked by a button ("Code" with an arrow next to it). Clicking this button reveals the underlying code from the R script that is being sourced in a given section.

# Install Libraries and Set Parameters

Before loading any data or beginning to construct the eGRID database, we install all necessary libraries used in subsequent scripts. Next, the eGRID year is defined, which controls which year of data is loaded from the raw data sources.

## Install required libraries

The script `install_libraries.R` detects all necessary libraries within the project using `renv::dependencies()`, checks for installation, and installs (if needed) and loads into the workspace.

```{r}
#| label: install-libraries.R
#| file: "scripts/1_production_model/install_libraries.R"
#| echo: false
```

```{r}
#| label: load-packages
#| echo: false

library(docstring)
library(dplyr)
library(ggiraph)
library(ggplot2)
library(gt)
library(gtExtras)
library(kableExtra)
library(knitr)
library(patchwork)
library(readxl)
library(stringr)
```

## Define eGRID year

The year of eGRID specified as the parameter "eGRID_year" within the YAML of the Quarto document. When a year value needs to be specified (e.g., when pulling relevant data from the CAMPD API), it is done so by calling `params$eGRID_year`.

**Current year setting: `r params$eGRID_year`**

## Load all helper functions

There are a set of helper functions used throughout the project. These are defined in the folder `scripts/functions`. The `docstring` package is used to provide documentation for functions, similar to typical package documentation. To view the documentation for a given function, run `docstring({function_name})`

```{r}
#| label: load-functions
#| echo: false

# sourcing each file in functions folder
functions <- list.files("scripts/functions")
purrr::walk(paste0("scripts/functions/", functions), ~ source(.x))
```

::: panel-tabset
### Overview

*Click on the tab to view the helper function names.*

### Helper Functions

```{r}
#| label: list-functions
#| echo: false

# listing function names
kable(stringr::str_remove(stringr::str_remove(functions, ".R"), "function_"),
      col.names = c("Helper Functions")) %>%
            kable_styling(full_width = F)
```
:::

# Load Data

## NEI

Document the difference between publically-available NEI data and the data we are using

Discuss how one might download it

## EIA

The U.S. Energy Information Administration (EIA), a part of the Department of Energy, collects and maintains energy-related data for policy making and for the public. We are using the same EIA data used in eGRID. If this data has not been downloaded previously, we can run the eGRID scripts to properly download and clean this data.

As of 2024, the EIA API does not contain the most detailed data available, which is necessary for the construction of eGRID. More detailed data for the EIA forms [923](https://www.eia.gov/electricity/data/eia923/), [860](https://www.eia.gov/electricity/data/eia860/), and [861](https://www.eia.gov/electricity/data/eia861/) are available as zipped excel file downloads on the EIA website. `data_load_eia.R` creates a new folder in the project folder called "raw_data". The zip files for each of the forms are downloaded and unzipped within this newly created folder. Each excel file contains several sheets that serve as the raw EIA data sources used to create eGRID.

```{r}
#| label: data-load-eia
#| file: "scripts/1_production_model/data_load_eia.R"
#| error: false
#| echo: fenced
```

The tables within EIA Files and Sheets display each of the unzipped raw files across the three EIA forms, including the sheets embedded within. Here we are interested only in the EIA-923 Data.

```{r}
#| label: custom-gt-print
#| echo: false

knit_print.gt <- function(x, ...) {
  stringr::str_c("<div style='all:initial;'>\n", gt::as_raw_html(x), "\n</div>") %>%
    knitr::asis_output()
}
registerS3method("knit_print", "gt_tbl", knit_print.gt, envir = asNamespace("gt"))
```

```{r}
#| label: create-eia-sheets-list

sheets_923  <- get_sheets("923")
tab_923  <- make_sheets_table(sheets_923, "923") 
 
sheets_used923 <-   c("Page 1 Generation and Fuel Data", # eia-923
                      "Page 1 Puerto Rico",
                      "Page 3 Boiler Fuel Data",
                      "Page 4 Generator Data",
                      "8C Air Emissions Control Info")

```

#### EIA Files and Sheets {#eia-files-sheets}

::::::: panel-tabset
#### Overview

*Click through the tabs above to view files represented from each EIA source.*

**EIA-923**: Data reported on fuel consumption and generation

#### EIA-923

```{r}
#| label: print-eia-923-sheets
#| tbl-cap: "EIA-923 sheets"
#| echo: false

tab_923
```

:::::::

## EIA-NEI Crosswalk

Describe EIA-NEI crosswalk here Determine where we get this data

```{r}
#| label: create-xwalk-summary
#| 
```



# Produce Data

## Unit Files

This script will produce unit file for PM~2.5~, NH~3~, and VOC emissions.

```{r}
#| label: unit-files-create
#| file: "scripts/2a_pm_nh3_voc/unit_file_create_pm_nh3_voc.R"
#| message: FALSE
```

```{r}
#| label: unit-file-table
#| include: false

unit_file_pm25 <- readr::read_rds(
           glue::glue("data/2a_pm_nh3_voc/outputs/{params$eGRID_year}/unit_file_pm25.RDS"))
```

### View Unit File Data

::::: panel-tabset
#### Overview

*Click through the tabs above to preview data contained within the unit file.*

#### Data Summary

```{r}
#| label: unit-file-summary

create_summary_table(unit_file_pm25)
```

:::::

## Plant Files

The plant file aggregates the unit data at the plant level using the eGRID dataseta and calcualtes () describe what it calculates

```{r}
#| label: plant-files-create
#| file: "scripts/2a_pm_nh3_voc/plant_file_create_pm_nh3_voc.R"
#| message: FALSE
```

```{r}
#| label: plant-file-table
#| include: false

plant_file_pm25 <- readr::read_rds(
           glue::glue("data/2a_pm_nh3_voc/outputs/{params$eGRID_year}/plant_file_pm25.RDS"))
```

### View Plant File Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data contained within the plant file.*

#### Data Summary

```{r}
#| label: plant-file-summary

create_summary_table(plant_file_pm25)
```

:::

## Region Aggregation Files

The plant file (`plant_file_pm25.RDS`) is aggregated to calculate the heat input, emissions, generation, fuel-based net generation, resource mix, and nameplate capacity from the plant-level data to the various aggregated levels: state (ST), balancing authority (BA), eGRID subregion (SRL), NERC region (NRL), and US level.

The aggregated files also calculate region specific output, input, combustion output, fuel-specific output, fuel-specific input, and nonbaseload output emissions rates. The aggregated level resource mix is estimated based on the summed generation by fuel values from the plant file. The nonbaseload generation is estimated by fuel type and resource mix.

```{r}
#| label: regional-aggregation-files-create
#| file: "scripts/2a_pm_nh3_voc/region_aggregation_create_pm_nh3_voc.R"
#| message: FALSE
```

```{r}
#| label: load-reg-agg-files
#| echo: false

st_agg  <- read_rds(
        glue::glue("data/2a_pm_nh3_voc/outputs/{params$eGRID_year}/state_aggregation_pm25.RDS"))
srl_agg <- read_rds(
        glue::glue("data/2a_pm_nh3_voc/outputs/{params$eGRID_year}/subregion_aggregation_pm25.RDS"))
us_agg  <- read_rds(
        glue::glue("data/2a_pm_nh3_voc/outputs/{params$eGRID_year}/us_aggregation_pm25.RDS"))
```

## View Aggregation Files Data

::: panel-tabset
#### Overview

*Click through the tabs above to preview data for each region aggregation.*

**ST**: State Aggregation

**SRL**: Subregion Aggregation

**US**: U.S. Aggregation

#### ST

```{r}
#| label: st-agg-summary

create_summary_table(st_agg)
```

#### SRL

```{r}
#| label: srl-agg-summary

create_summary_table(srl_agg)
```

#### US

```{r}
#| label: us-agg-summary

create_summary_table(us_agg)
```
:::

# Produce Final Dataset

The data is formatted into an Excel file that contains all eight levels of data aggregation. For headers, we add descriptions and label conventions to maintain consistency with previous eGRID releases. Formatting is applied for both imperial unit version and the metric unit version.

The final output file is `r glue::glue("egrid{params$eGRID_year}_data.xlsx")`.

```{r}
#| label: final-formatting
#| file: "scripts/2a_pm_nh3_voc/final_formatting_pm_nh3_voc.R"
#| message: FALSE
```

# we could at some point show the subregion plots as well
